\chapter{Multi-Path TL Network Solver}
\label{ch:network_solver}

Chapter~\ref{ch:sim_architecture} established the 1D ABCD cascade as a transmission-line model of the protein backbone.
While this cascade predicts equilibrium size ($R_g$ to within 0.5--7.6\%) and secondary structure content (22--34\%), it has an intrinsic limitation: \emph{there is only one propagation path}.
Every impedance mismatch along the backbone creates a backwards-reflected wave that adds directly to $|S_{11}|^2$, and the Y-shunt coupling terms that model H-bonds and sidechain contacts cannot create \emph{alternative propagation paths}---only modify the existing cascade.

This chapter presents the solution: upgrading from a 1D cascade to a 2D S-parameter network, where every bond type---backbone, H-bond, through-space contact---becomes a full transmission-line segment connecting two nodes in an admittance matrix.

% ═══════════════════════════════════════════════════════════════
\section{Architecture: From Cascade to Network}
\label{sec:cascade_to_network}

\subsection{The Y-Shunt Balance Theorem}
\label{sec:yshunt_balance}

The 1D engine models non-bonded contacts as shunt admittances at backbone junctions:
\begin{equation}
    Y_\text{shunt}(i) = \sum_{j \neq i} \frac{\kappa \, m_{ij} \, C_\text{sat}(d_{ij})}{d_{ij}^2} \cdot S_\text{env}(d_{ij})
    \label{eq:yshunt}
\end{equation}
where $\kappa = 1/2$ (critical coupling), $m_{ij}$ is the conjugate impedance match, $C_\text{sat}$ is the Axiom~4 dielectric saturation factor, and $S_\text{env}$ is the long-range saturation envelope.

However, Y-shunt terms have a \emph{double-edged} effect: they absorb energy from propagating modes (lowering $|S_{11}|$), but they also damp the standing-wave resonances that drive secondary structure formation.
Beyond a critical shunt magnitude, additional coupling \emph{degrades} SS accuracy---the Y-Shunt Balance Theorem (Section~\ref{sec:1d_limitations}).

\subsection{Network Topology}
\label{sec:network_topology}

The 2D engine replaces Y-shunt perturbations with full TL segments that create \emph{alternative propagation paths} through the network.
Each segment has characteristic impedance $Z_c$, propagation constant $\gamma = \alpha + j\beta$, and length $\ell$:

\begin{itemize}
    \item \textbf{Backbone segments} ($3N-1$ total): N$_i$--C$\alpha_i$, C$\alpha_i$--C$_i$, C$_i$--N$_{i+1}$, with $Z_c$ from bond impedance $\sqrt{m_\text{bond}/n_e}$ and chirality phase correction $\delta_\chi$
    \item \textbf{H-bond cross-links} ($N^2$ potential, gated by proximity): N$_i$--C$_j$ for $|i-j| \geq 3$, with $Z_c = Z_\text{avg}/(2Q)$ and $\kappa_\text{HB} = 1/(2Q) = 1/14$ coupling
    \item \textbf{Through-space TL segments}: C$\alpha_i$--C$\alpha_j$ for $|i-j| \geq 3$, with impedance from conjugate $Z$-match and Axiom~4 dielectric saturation
    \item \textbf{Solvent ground loads}: Exposed C$\alpha$ nodes terminated with Debye $Z_\text{water}(\omega)$
    \item \textbf{Peptide-plane coupling}: Adjacent backbone shunt $Y_\text{pep} = \lambda_R \kappa_\text{HB} \cos(\hat{n}_i \cdot \hat{n}_{i+1})$
\end{itemize}

\subsection{Y-Parameter Formulation}
\label{sec:y_param}

Each TL segment maps to a $2 \times 2$ admittance matrix:
\begin{equation}
    \mathbf{Y}_\text{seg} = \begin{pmatrix}
        Y_c \coth(\gamma\ell) & -Y_c \operatorname{csch}(\gamma\ell) \\
        -Y_c \operatorname{csch}(\gamma\ell) & Y_c \coth(\gamma\ell)
    \end{pmatrix}, \qquad Y_c = 1/Z_c
    \label{eq:y_matrix_tl}
\end{equation}
At each node, Kirchhoff's current law requires the sum of all connected Y-matrices.
The global nodal admittance matrix $\mathbf{Y}_\text{global}$ ($3N \times 3N$, complex) is assembled by stamping each segment's $2\times 2$ Y-matrix at its node indices.

\subsection{S$_{11}$ via Schur Complement}
\label{sec:schur}

The input port is at node~0 (N-terminus nitrogen, N$_0$).
All other $3N-1$ nodes are internal.
The 1-port input admittance is obtained by Schur complement reduction:
\begin{equation}
    Y_\text{in} = Y_{00} - \mathbf{Y}_{0x} \, \mathbf{Y}_{xx}^{-1} \, \mathbf{Y}_{x0}
    \label{eq:schur}
\end{equation}
where $\mathbf{Y}_{xx}$ is the $(3N-1) \times (3N-1)$ internal block, solved via \texttt{jnp.linalg.solve} for numerical stability.
The reflection coefficient follows:
\begin{equation}
    |S_{11}|^2 = \left| \frac{1 - Z_0 Y_\text{in}}{1 + Z_0 Y_\text{in}} \right|^2
    \label{eq:s11_network}
\end{equation}
Multi-frequency averaging over $\omega/\omega_0 \in \{0.5, 1.0, 1.7\}$ produces the final loss, modulated by the global $P_C$ packing saturation (Axiom~4 trace reversal, identical to Chapter~\ref{ch:sim_architecture}).

% ═══════════════════════════════════════════════════════════════
\section{Compaction Physics}
\label{sec:compaction}

The through-space C$\alpha$--C$\alpha$ TL segments provide the compaction driving force.
Their impedance encodes three physical layers:

\paragraph{Conjugate impedance matching.}
For residues $i, j$ with complex impedances $Z_i, Z_j$:
\begin{equation}
    m_{ij} = \max\!\left(0,\; \frac{\operatorname{Re}(Z_i Z_j^*)}{|Z_i||Z_j|}\right) \in [0, 1]
    \label{eq:conj_match}
\end{equation}
Hydrophobic pairs ($m_{ij} \to 1$) create low-impedance through-space paths that attract.
Like-charged pairs ($m_{ij} = 0$) create no path---repulsion emerges from the S$_{11}$ gradient at close range.

\paragraph{Axiom~4 dielectric saturation.}
Close-contact amplification:
\begin{equation}
    C_\text{sat} = 1 + \frac{m_{ij}}{\sqrt{1 - (d_0/d_{ij})^2}}
    \label{eq:c_sat_network}
\end{equation}
Well-matched close pairs get amplified coupling; mismatched close pairs do not.

\paragraph{Long-range saturation envelope.}
Same Axiom~4 operator as galactic rotation:
\begin{equation}
    S_\text{env}(d) = \sqrt{1 - (d/R_\text{burial})^2}, \qquad R_\text{burial} = 2d_0 = 7.6\;\text{\AA}
    \label{eq:sat_envelope}
\end{equation}
Beyond $R_\text{burial}$, coupling decays to zero---preventing the ``dark matter halo'' of over-compaction.

% ═══════════════════════════════════════════════════════════════
\section{Benchmark Results}
\label{sec:2d_benchmark}

Table~\ref{tab:2d_benchmark} compares the 1D ABCD cascade (Chapter~\ref{ch:sim_architecture}) with the 2D TL network on four benchmark proteins.

\begin{table}[H]
\centering
\caption{1D ABCD cascade vs 2D S-parameter network.
All constants identical between engines; only the network topology differs.
$R_g$ target from $\eta_\text{eq} = P_C(1-\nu)$.
10\,000 gradient steps, 3 random starts, Adam optimiser ($\text{lr}=2\times 10^{-3}$).}
\label{tab:2d_benchmark}
\begin{tabular}{@{}l c r r r r r r@{}}
\toprule
\textbf{Protein} & $N$ & \multicolumn{2}{c}{\textbf{$R_g$ error}} & \multicolumn{2}{c}{\textbf{SS \%}} & \multicolumn{2}{c}{\textbf{RMSD (\AA)}} \\
\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
 & & 1D & 2D & 1D & 2D & 1D & 2D \\
\midrule
Trp-cage (1L2Y) & 20 & 3.8\% & 10.8\% & 34 & 6 & 5.65 & 5.87 \\
Villin HP35 (1YRF) & 35 & 0.5\% & 11.4\% & 24 & \textbf{27} & 7.61 & 8.44 \\
GB1 (1PGA) & 56 & 5.5\% & 10.9\% & 22 & 17 & 9.89 & 10.51 \\
Ubiquitin (1UBQ) & 76 & 7.6\% & 11.8\% & 27 & 16 & 10.83 & 11.26 \\
\midrule
\textbf{Mean} & & 4.4\% & 11.2\% & 26.8 & 16.5 & 8.50 & 9.02 \\
\midrule
\multicolumn{2}{@{}l}{\textbf{$|S_{11}|^2$ (loss)}} & \multicolumn{2}{c}{0.82 $\to$ 0.075} & \multicolumn{4}{c}{\textit{15$\times$ lower reflection}} \\
\bottomrule
\end{tabular}
\end{table}

\section{Analysis}
\label{sec:2d_analysis}

\subsection{Where the Network Wins}
\begin{enumerate}
    \item \textbf{Impedance matching}: The network $|S_{11}|^2$ is 15$\times$ lower than the cascade (0.075 vs 0.82), confirming that multi-path wave propagation provides fundamentally better impedance matching.
    \item \textbf{Villin secondary structure}: 27\% vs 24\%---the first case where the 2D topology outperforms the 1D cascade on SS.
    \item \textbf{JIT scalability}: Compilation time is nearly constant (1.8--2.3\,s) regardless of $N$, because the vectorised Y-matrix assembly scales as $O(N^2)$ tensor operations rather than $O(N^2)$ traced Python loops.
\end{enumerate}

\subsection{Where the Cascade Still Wins}
\begin{enumerate}
    \item \textbf{$R_g$ accuracy}: The 1D engine achieves 0.5--7.6\% error; the 2D engine consistently over-compacts at $\sim$11\%.
    The through-space coupling may need a size-dependent attenuation floor.
    \item \textbf{SS for small proteins}: Trp-cage SS dropped from 34\% to 6\%.
    With $N=20$, the $N^2$ through-space TL segments create too many coupling paths relative to the $3N-1$ backbone segments, drowning the resonance structure.
    \item \textbf{Speed}: 6$\times$ slower per optimisation step ($\sim$90\,s vs 14\,s) due to the $(3N-1) \times (3N-1)$ matrix solve at each frequency.
\end{enumerate}

\subsection{Physical Interpretation}

The 1D cascade has higher $|S_{11}|^2$ but better structural accuracy because its Y-shunt couplings, while physically approximate, preserve the standing-wave resonance structure that drives SS emergence.
The 2D network has lower $|S_{11}|^2$ but the optimizer finds minima where the multi-path propagation ``short-circuits'' the backbone instead of setting up the precise resonance patterns needed for helices and sheets.

This suggests the next step is not adding more coupling paths, but improving how existing paths interact---enforcing the \emph{resonance condition} that standing waves in the backbone must match the periodicity of secondary structure elements.

% ═══════════════════════════════════════════════════════════════
\section{Roadmap}
\label{sec:2d_roadmap}

\begin{enumerate}
\item \textbf{Resonance-aware coupling}: Weight through-space segments by their alignment with backbone standing-wave nodes, so coupling reinforces rather than disrupts SS.
\item \textbf{$\beta$-sheet TL segments}: Currently only $\alpha$-helix N$_i$--C$_j$ H-bonds form; antiparallel $\beta$-sheet requires C$_i$--N$_j$ pairing (reversed polarity).
\item \textbf{3D Yee-lattice FDTD}: Replace the lumped Y-matrix with a spatial impedance grid where $\varepsilon(x) = Z_\text{topo}$ and the protein backbone perturbs the lattice---capturing wave diffraction around the structure.
\item \textbf{Hybrid 1D$+$2D}: Use the 1D cascade for backbone propagation (preserving SS) and the 2D network only for long-range contacts (providing compaction), combining the strengths of both architectures.
\end{enumerate}
