\chapter*{Nomenclature and Fundamental Constants}
\addcontentsline{toc}{chapter}{Nomenclature and Fundamental Constants}

\section*{Universal Hardware Constants}
The following constants define the constitutive, physical properties of the \textit{Discrete Amorphous Manifold} ($M_A$). In the SVF framework, these are the bulk engineering specifications of the vacuum substrate.



\begin{tabularx}{\textwidth}{|l|X|l|l|}
\hline
\textbf{Symbol} & \textbf{Name} & \textbf{Value (SI)} & \textbf{Hardware Role} \\ \hline
$\Lvac$ & Lattice Inductance & $\approx 1.26 \times 10^{-6}$ H/m & $\mu_0$ (Inertial Density) \\ \hline
$\Cvac$ & Lattice Capacitance & $\approx 8.85 \times 10^{-12}$ F/m & $\epsilon_0$ (Elastic Potential) \\ \hline
$\Zvac$ & Characteristic Impedance & $\approx 376.73\,\Omega$ & $\sqrt{\Lvac/\Cvac}$ (Base Load) \\ \hline
$\lp$ & Lattice Pitch & $\approx 1.62 \times 10^{-35}$ m & Nodal Spacing (Nyquist Limit) \\ \hline
$\Wcut$ & Saturation Frequency & $2 / \sqrt{\Lvac \Cvac \lp^2}$ & Global Slew Rate ($c/\lp$) \\ \hline
\end{tabularx}

\section*{Emergent Variables and Tensors}
These variables describe the behavior of topological defects (matter) and signal propagation within the hardware layers.

\begin{itemize}
    \item \textbf{$\epsilon_{\mu\nu}$ (Metric Strain Tensor)}: Quantifies the physical displacement of manifold nodes from ground-state equilibrium. This recasts the abstract "curvature" of General Relativity as a measurable mechanical strain of the hardware nodes.
    \item \textbf{$h$ (Topological Helicity)}: An integer representing the quantized phase-twist of a defect. This is the mechanical identity of \textbf{Electric Charge} ($q$).
    \item \textbf{$\nu_{sat}$ (Saturation Threshold)}: The frequency at which a node enters a non-linear regime, clamping energy into a stationary standing wave. This "trapped flux" is measured as \textbf{Rest Mass}.
    \item \textbf{$v_g$ (Group Velocity)}: The propagation speed of energy through the lattice nodes, subject to frequency-dependent attenuation:
    \begin{equation}
        v_g = c \sqrt{1 - \left(\frac{\omega}{\Wcut}\right)^2}
    \end{equation}
\end{itemize}



\section*{Operational Acronyms}
\begin{tabularx}{\textwidth}{|l|l|X|}
\hline
\textbf{Acronym} & \textbf{Full Term} & \textbf{Mechanical Mapping} \\ \hline
\textbf{B-EMF} & Back-Electromotive Force & The hardware origin of \textbf{Inertia}. \\ \hline
\textbf{CBE} & Chiral Bias Equation & The law governing spin-dependent impedance. \\ \hline
\textbf{MA} & Amorphous Manifold & The stochastic, discrete hardware substrate. \\ \hline
\textbf{VSI} & Variable Spacetime Impedance & The state of the manifold under metric strain. \\ \hline
\textbf{TVS} & Transient Voltage Suppressor & Analogy for high-frequency \textbf{Weak Force} clamping. \\ \hline
\end{tabularx}