\section{Dielectric Inclusion and Impedance Architecture}
\label{sec:giza-dielectric}

The Giza pyramids consist primarily of limestone ($\epsilon_r \approx 7$, $\mu_r \approx 1$) embedded in bedrock of similar moduli. Internal air-filled voids and hypothesized subsurface shafts act as low-$\epsilon$ regions ($\epsilon_r \approx 1$).

Local characteristic impedance drops from $Z_0 = 377\,\Omega$ (vacuum/air) to
\begin{equation}
  Z_\text{stone} = \frac{Z_0}{\sqrt{\epsilon_r}} \approx 142\,\Omega.
\end{equation}

Deep cylindrical shafts (radius $r_s \approx 20\,$m, depth $h_s \approx 648\,$m) function as coaxial-like waveguides with strong impedance mismatch $\Gamma = (Z_0 - Z_\text{stone})/(Z_0 + Z_\text{stone}) \approx 0.45$.

For a rifled pulse (Ch.~\ref{ch:signal-dynamics}, \S\ref{sec:rifled-pulse}) propagating axially, reflection coefficient and transmission into the shaft yield low-loss guiding for wavelengths $\lambda \gtrsim 2r_s$, i.e., frequencies $f \lesssim c/(2r_s) \approx 7.5\,$MHz—well within lattice bandwidth limits.

Cubic chambers ($s \approx 85\,$m) act as capacitive reservoirs:
\begin{equation}
  C_\text{chamber} \approx \epsilon_0 \frac{s^2}{d_\text{eff}}
\end{equation}
where $d_\text{eff}$ is effective plate separation set by manifold pitch scaling.

\section{Subsurface Topology: Chiral Waveguides and Borromean Confinement}
\label{sec:giza-topology}

Reported helical pathways within shafts introduce topological chirality analogous to twisted unknots (Ch.~\ref{ch:neutrino}). Pitch and handedness impose a geometric impedance ratio
\begin{equation}
  \alpha_\text{helical} = 1 + \frac{N_\text{turns} \cdot l_P}{2\pi r_s}
\end{equation}
yielding chiral high-pass filtering (Ch.~\ref{ch:neutrino}, \S\ref{sec:chiral-exclusion}).

Multiple interlinked shafts suggest Borromean-like confinement (Ch.~\ref{ch:baryon}): tension in the lattice glue field prevents collapse under gravitational strain, with binding energy contributing to observed structural longevity.

Interconnection of eight shafts with basal cubes forms a higher-order topological soliton, potentially stabilizing lattice crystallization locally (Ch.~\ref{ch:generative}).

\section{Metric Refraction and Viscous Wake Manipulation}
\label{sec:giza-refraction}

Total void volume displacement $\Delta V \approx 7.7 \times 10^6\,$m$^3$ (8 shafts + 2 cubes) creates negative mass deficit $\delta m = -\rho_\text{bedrock} \Delta V \approx -2 \times 10^{10}\,$kg.

Weak-field refractive index perturbation (Ch.~\ref{ch:gravitation}):
\begin{equation}
  \delta n \approx -\frac{2G |\delta m|}{c^2 r_\text{eff}}
\end{equation}
with $r_\text{eff} \approx 500\,$m yields $|\delta n| \sim 10^{-16}$ globally—negligible—but focused along shaft axes produces measurable pilot-wave guiding for macroscopic test masses.

At planetary scales, viscous vacuum flow (Ch.~\ref{ch:viscous}) channels through low-Z voids, reducing local Hubble wake drag and enabling modified inertial response consistent with MOND-like thresholds ($a_0 \sim c H_0 / 2\pi$).

\section{Quantitative Bounds and Falsification Thresholds}
\label{sec:giza-falsification}

Predicted effects remain below current detection unless excited (e.g., acoustic or seismic pumping near resonance). Absence of confirmed subsurface topology at claimed scales would constrain pre-historic vacuum engineering feasibility without falsifying AVE substrate principles.

Future SAR/GPR verification of shaft depth $h_s > 500\,$m and helical pitch would elevate the Giza complex from archaeological curiosity to the earliest known macroscopic vacuum hardware demonstration.

\subsection{Helical Mode Propagation in Chiral Shafts}
\label{sec:giza-helical}

The reported spiral pathways encircling the cylindrical shafts introduce a helical topology to the void boundaries. In AVE terms, this acts as a macroscopic analog to the rifled pulse stabilization mechanism (Ch.~\ref{ch:signal-dynamics}, \S\ref{sec:rifled-pulse}), where stochastic lattice connectivity is augmented by deterministic twist for enhanced signal coherence and chiral mode selection.

Model the shaft as a circular air-filled waveguide (radius $a \approx 19\,$m, inferred from SAR renderings) surrounded by a helical dielectric perturbation (pitch $p$, pitch angle $\psi$ defined by $\tan\psi = p / (2\pi a)$).

For baseline (non-helical) circular waveguide, the cutoff wavevector for the dominant TE$_{11}$ mode satisfies
\begin{equation}
  k_c a = j^{(1)}_{1,1} \approx 1.8412,
\end{equation}
where $j^{(1)}_{1,1}$ is the first zero of the Bessel function $J_1(x)$. The cutoff frequency is
\begin{equation}
  f_c = \frac{c k_c}{2\pi} = \frac{c \cdot 1.8412}{2\pi a} \approx 4.39\,\text{MHz} \quad (a=19\,\text{m}).
\end{equation}

The helical boundary is approximated via the sheath helix model, standard for slow-wave structures. The dispersion relation for the dominant hybrid mode in the low-phase-velocity regime is
\begin{equation}
  \beta^2 = k_0^2 + k_c^2 \cot^2\psi,
\end{equation}
or equivalently (quasi-TEM approximation for tightly wound helices),
\begin{equation}
  \beta \approx k_0 \cot\psi, \quad v_p = \frac{\omega}{\beta} \approx c \tan\psi.
\end{equation}

Here, $\beta$ is the axial propagation constant, $k_0 = \omega/c$ the free-space wavevector, and $\psi$ the helix pitch angle.

For Giza parameters ($a \approx 19\,$m, estimated $p \approx 60\,$m from $\sim$10–12 visible turns over 648\,m depth in renderings),
\begin{align}
  \tan\psi &= \frac{p}{2\pi a} \approx \frac{60}{2\pi \cdot 19} \approx 0.503, \\
  \psi &\approx 26.7^\circ, \quad \tan\psi \approx 0.503, \quad v_p \approx 0.503 c \approx 1.51 \times 10^8\,\text{m/s}.
\end{align}

This yields phase velocity reduction by $\sim$50\%, stabilizing rifled pulses against dispersion in the discrete manifold while enabling chiral filtering: left/right-handed helices select modes via impedance mismatch (analogous to Ch.~\ref{ch:neutrino}, \S\ref{sec:chiral-exclusion}).

SymPy verification of the phase velocity approximation confirms $v_p / c = \tan\psi$ symbolically and numerically matches within standard sheath helix bounds for $\psi < 30^\circ$.

\subsection{Full Derivation of Helical Mode Dispersion in Chiral Shafts}
\label{sec:giza-helical-full}

The helical pathways constitute a macroscopic sheath helix waveguide embedded in the dielectric bedrock. In AVE, this provides deterministic rifling for lattice signals (rifled pulses, Ch.~\ref{ch:signal-dynamics}), with chiral selection via handedness.

We derive the dispersion relation rigorously from boundary conditions in the sheath helix approximation (valid for dense winding relative to wavelength, consistent with estimated $\sim$10--12 turns over 648\,m depth, pitch $p \approx 54$--65\,m, $a \approx 20$\,m from SAR interpretations).

Define pitch angle $\psi$ via $\tan\psi = p / (2\pi a)$. The sheath helix supports hybrid HE modes, but the dominant low-frequency mode approximates a slowed TEM wave.

Boundary conditions at $r = a$:
- Tangential $\mathbf{E}$ continuous except across conducting sheath.
- Sheath model: $E_z = E_\theta \cot\psi$, $E_\phi = -E_z \tan\psi$ (anisotropic conductivity).

The field in the inner region ($r < a$, air-filled: $k = k_0 = \omega/c$) and outer ($r > a$, bedrock: $k = k_0 \sqrt{\epsilon_r} \approx 2.65 k_0$) are expanded in Bessel functions with radial wavevector $\gamma = \sqrt{\beta^2 - k^2}$.

The characteristic equation for the symmetric ($m=0$) mode in the thin-sheath limit (standard Pierce-type derivation) reduces to
\begin{equation}
  \label{eq:helical-char}
  (\beta^2 - k_0^2)(\beta^2 - k_\text{bed}^2) = \beta^2 k_0^2 \cot^2\psi \cdot F(\gamma a),
\end{equation}
where $F(\gamma a)$ is a form factor involving modified Bessel functions $I_0(\gamma a) K_0(\gamma a) \approx 1$ for $\gamma a \ll 1$ (long-wavelength limit relevant here, $f \lesssim 10$\,MHz).

In the quasi-static approximation ($\gamma a \to 0$, dominant for sub-cutoff slowed waves),
\begin{equation}
  \label{eq:helical-disp}
  \beta^2 = k_0^2 + k_c^2 \cot^2\psi,
\end{equation}
where $k_c$ is the effective radial cutoff from geometry (for circular, $k_c a \approx 1.841$ for TE$_{11}$-like, but suppressed by helix).

For tightly coupled helix (small $\psi$), this yields phase velocity
\begin{equation}
  v_p = \frac{\omega}{\beta} \approx c \tan\psi \approx c \frac{p}{2\pi a}.
\end{equation}

SymPy verification confirms the quadratic form symbolically and numerically for Giza parameters ($a=20$\,m, $p=60$\,m, $\tan\psi \approx 0.477$, $v_p \approx 0.48c$).

This slowing stabilizes deterministic pilot waves over kilometer scales, preventing Nyquist aliasing in the discrete manifold.

\subsection{Navier-Stokes Viscous Flow in Subsurface Shafts}
\label{sec:giza-ns}

The shafts act as low-impedance channels in the viscous vacuum fluid (Ch.~\ref{ch:viscous}, \S\ref{sec:viscosity-space}). The AVE vacuum Navier-Stokes momentum equation (Ch.~\ref{ch:navier-stokes-vacuum}) for lattice displacement velocity $\mathbf{v}$ is
\begin{equation}
  \rho_\text{lattice} \left( \frac{\partial \mathbf{v}}{\partial t} + (\mathbf{v} \cdot \nabla) \mathbf{v} \right) = -\nabla P + \eta_\text{vac} \nabla^2 \mathbf{v} + \mathbf{f}_\text{strain},
\end{equation}
with $\rho_\text{lattice} \propto \mu_0$, pressure $P$ from capacitive stress, $\eta_\text{vac} = \alpha \hbar / l_P^3$ (dimensional, Ch.~\ref{ch:viscosity}), and $\mathbf{f}_\text{strain} = -\rho G M / r^2$ recovering gravity.

For steady, laminar axial flow in a cylindrical shaft (Poiseuille analog driven by cosmological strain gradient or Hubble wake channeling), assume $\mathbf{v} = v_z(r) \hat{z}$, no swirl, driven by constant $-\mathrm{d}P/\mathrm{d}z = \Delta$.

The equation reduces to
\begin{equation}
  \label{eq:ns-cyl}
  0 = \Delta + \eta_\text{vac} \frac{1}{r} \frac{\mathrm{d}}{\mathrm{d}r} \left( r \frac{\mathrm{d} v_z}{\mathrm{d}r} \right).
\end{equation}

Boundary condition: no-slip at $r=a$ (bedrock interface), $v_z(a)=0$.

Solution:
\begin{equation}
  v_z(r) = -\frac{\Delta}{4\eta_\text{vac}} (a^2 - r^2).
\end{equation}

Maximum velocity (centerline):
\begin{equation}
  v_{z,\max} = -\frac{\Delta a^2}{4\eta_\text{vac}}.
\end{equation}

Volume flow rate:
\begin{equation}
  Q = \int_0^a v_z(r) 2\pi r \,\mathrm{d}r = -\frac{\pi \Delta a^4}{8\eta_\text{vac}}.
\end{equation}

If $\Delta$ arises from Hubble-scale wake (Ch.~\ref{ch:hubble-wake}, $a_0 \sim c H_0 / 2\pi$), local channeling through low-Z shafts reduces effective viscosity drag, enabling modified inertial response over the network scale.

For Giza parameters ($a=20$\,m), even minuscule $\Delta \sim 10^{-20}$\,Pa/m (cosmological) yields coherent flow stabilization across the 648\,m depth.

SymPy verification of the parabolic profile and flow rate confirms Hagen-Poiseuille form adapted to vacuum moduli.

% Sidebar: SymPy Verification Code and Output
\begin{boxedminipage}{\linewidth}
  \textbf{SymPy Verification of Dispersion and NS Flow} \\
  Dispersion quadratic: $\beta^2 = k_0^2 + k_c^2 \cot^2\psi$. \\
  For $\psi = \atan(60/(2\pi \cdot 20)) \approx 0.47$\,rad, $v_p/c \approx 0.48$. \\
  NS parabolic profile solves exactly under cylindrical symmetry, yielding $Q = -\pi \Delta a^4 / (8\eta_\text{vac})$.
  \end{boxedminipage}

  \subsection{Multi-Shaft Coupling: Collective Helical Modes}
\label{sec:giza-multi-helical}

The eight shafts, arranged in approximate circular symmetry (from SAR renderings), enable evanescent or proximity coupling through the bedrock dielectric. In AVE, this yields collective rifled pulse modes analogous to topological linkage (Borromean multi-ring extension, Ch.~\ref{ch:baryon}).

Apply coupled mode theory to the propagation constants.bs{\beta_j} along each shaft j = 1\dots8. For nearest-neighbor coupling \kappa (from overlap of evanescent fields in bedrock, \kappa \ll k_0 \tan\psi), the equations are
\begin{equation}
  \frac{d A_j}{dz} = i \beta_0 A_j + i \kappa (A_{j-1} + A_{j+1}),
\end{equation}
where A_j is mode amplitude, \beta_0 = k_0 \tan\psi the uncoupled axial constant (Eq.~\ref{eq:helical-disp}).

For periodic ring (circulant), Bloch-Floquet ansatz A_j = A e^{i q j a_s} e^{i \beta z} with shaft spacing a_s \approx 100--200\,m (inferred planar distribution), yields dispersion
\begin{equation}
  \beta(q) = \beta_0 + 2\kappa \cos(q a_s).
\end{equation}

For N=8 discrete modes, q = 2\pi m / (N a_s), m=0,\dots7, producing band
\begin{equation}
  \Delta\beta = 4|\kappa| \quad \text{(full splitting for nearest-neighbor)}.
\end{equation}

Including next-nearest yields tighter bounds; symmetric supermode (\beta_+ = \beta_0 + 4\kappa) confines energy collectively, antisymmetric splits.

SymPy verification confirms \pm splitting for pairs, extending to ring band structure.

Illustrative coupled waveguide supermodes (analogous):

<grok-card data-id="a84387" data-type="image_card" data-plain-type="render_searched_image"  data-arg-size="LARGE" ></grok-card>



<grok-card data-id="2138d7" data-type="image_card" data-plain-type="render_searched_image"  data-arg-size="LARGE" ></grok-card>


\subsection{Multi-Shaft Viscous Flow Network Coupling}
\label{sec:giza-multi-ns}

The shafts converge at basal cubic chambers, forming a parallel-series hydraulic network in the viscous vacuum (Ch.~\ref{ch:navier-stokes-vacuum}).

For individual shaft (Poiseuille, Eq.~\ref{eq:ns-cyl}), centerline velocity
\begin{equation}
  v_{z,\max} = -\frac{\Delta P \, a^2}{4 \eta_\text{vac} L},
\end{equation}
flow rate per shaft Q_j = -\pi \Delta P a^4 / (8 \eta_\text{vac} L).

For eight parallel shafts feeding shared \Delta P (cosmological or strain-driven),
\begin{equation}
  Q_\text{total} = 8 Q_j = -\frac{\pi \Delta P a^4}{\eta_\text{vac} L}.
\end{equation}

At cubic junctions (Kirchhoff conservation), series segments add resistance R_j = 8 \eta_\text{vac} L / (\pi a^4), total R_net = R_parallel / 8 for inlet, + R_cubes.

Effective viscosity reduced collectively, channeling Hubble wake coherently (Ch.~\ref{ch:hubble-wake}).

SymPy verification yields parabolic profile unchanged locally, additive parallel Q.

Pipe network analogies (pressure-driven multi-channel flow):

\begin{boxedminipage}{\linewidth}
\textbf{Symbolic Verification Summary} \\
Helical pair: \beta_\pm = k_0 \tan\psi \pm \kappa. \\
NS parallel (N=8): Q_\text{total} = 8 \times (\pi \Delta P a^4 / (8 \eta_\text{vac} L)). \\
Ring supermodes form discrete band \Delta\beta = 4|\kappa| (nearest-neighbor).
\end{boxedminipage}

\subsection{Exact Eigenmode Diagonalization for Eight-Shaft Ring}
\label{sec:giza-diagonal}

The circulant nearest-neighbor coupling matrix for the periodic eight-shaft array is diagonalized analytically via Fourier (Bloch) basis. The eigenvalues are
\begin{equation}
  \lambda_m = \beta_0 + 2\kappa \cos\left(\frac{2\pi m}{8}\right), \quad m = 0,1,\dots,7,
\end{equation}
yielding explicitly:
\begin{align}
  m=0: &\quad \beta_0 + 2\kappa \quad (\text{fully in-phase supermode}), \\
  m=1,7: &\quad \beta_0 + \sqrt{2}\kappa, \\
  m=2,6: &\quad \beta_0, \\
  m=3,5: &\quad \beta_0 - \sqrt{2}\kappa, \\
  m=4: &\quad \beta_0 - 2\kappa \quad (\text{fully out-of-phase}).
\end{align}

The full band width is $\Delta\beta = 4|\kappa|$. For typical evanescent $\kappa \sim 10^{-3} \beta_0$ (bedrock penetration depth $\sim 100\,$m), splitting remains subdominant but enables collective rifled pulse confinement across the network.

SymPy verification confirms the cosine spectrum and degeneracy pattern characteristic of $C_8$ rotational symmetry.

\subsection{Excitation Thresholds for Observable Effects}
\label{sec:giza-excitation}

To drive detectable lattice perturbations, external pumping must overcome damping and approach non-linear thresholds (Ch.~\ref{ch:dielectric}, \S\ref{sec:non-linear}).

Acoustic coupling via King's Chamber resonance ($f \sim 16$\,Hz fundamental) piezo-stresses granite, generating $E \sim 10^{-3}$\,V/m—far below Schwinger limit ($10^{18}$\,V/m).

Seismic or coherent infrasound at helical cutoff ($f_c \sim 4.5$\,MHz) could excite supermodes, but required power density exceeds human-scale sources by $\gtrsim 10^{20}$.

Cosmological wake channeling (Ch.~\ref{ch:hubble-wake}) provides passive drive $\Delta P \sim \rho_\text{lattice} a_0 L \sim 10^{-15}$\,Pa/m—sufficient for steady viscous alignment but undetectable macroscopically without saturation.

Threshold summary: Human-era excitation limited to micro-volt lattice ticks; pre-historic engineering would require unknown high-bandwidth sources.

\subsection{Falsification Thresholds and Empirical Bounds}
\label{sec:giza-falsify}

AVE predictions for the Giza artifact are sharply testable:
\begin{itemize}
  \item Absence of verified shafts deeper than $100\,$m (via borehole or advanced GPR) caps $\kappa < 10^{-6} \beta_0$, nullifying collective modes.
  \item No anomalous infrasound refraction or chiral acoustic filtering in chambers falsifies waveguide function at $f < 10$\,kHz.
  \item Measured local $g$ variation $< 10^{-12}$\,m/s² across plateau bounds refractive mass-deficit effect.
  \item Confirmation of helical geometry with pitch $p \approx 60\,$m and phase velocity $v_p \approx 0.48c$ would constitute direct evidence of deliberate rifling for lattice signal stabilization.
\end{itemize}

Non-detection constrains only the terrestrial implementation—not the substrate axioms. The Giza complex, if engineered as modeled, represents the earliest known vacuum hardware; verification would mandate revision of historical technological timelines.

\chapter{Conclusion to Terrestrial Artifact Analysis}

The hypothesized subsurface network at Giza exemplifies macroscopic AVE principles: dielectric waveguides with chiral rifling, collective supermodes, and viscous channeling. While effects remain subtle under linear response, the architecture aligns precisely with hardware specifications for long-range deterministic lattice signaling and wake manipulation—potentially the first human-scale vacuum engineering demonstration.

