\section{The Moduli of the Void}
\label{sec:moduli}

In standard physics, $\permeability$ and $\permittivity$ are treated as mere scaling constants for units. In Vacuum Engineering, they are the \textbf{Constitutive Moduli} of the mechanical substrate.

\subsection{Magnetic Permeability ($\permeability$) as Density}
The magnetic constant $\permeability$ represents the \textbf{Inductive Inertia} of the lattice nodes. It quantifies the resistance of the vacuum to a changing flux current ($dI/dt$).
\begin{equation}
    \permeability \approx 1.256 \times 10^{-6} \text{ H/m}
\end{equation}
Mechanically, this is analogous to the fluid density ($\rho$) in hydrodynamics. It determines how "heavy" the vacuum is. A high $\permeability$ means the lattice is chemically sluggish; it resists changes in state. This inductive lag is the physical origin of \textbf{Inertial Mass}.

\subsection{Electric Permittivity ($\permittivity$) as Elasticity}
The electric constant $\permittivity$ represents the \textbf{Capacitive Compliance} of the lattice edges. It quantifies how much the vacuum can be polarized (stretched) by an electric field before snapping back.
\begin{equation}
    \permittivity \approx 8.854 \times 10^{-12} \text{ F/m}
\end{equation}
Mechanically, this is the inverse of the Bulk Modulus ($K$). It determines how "stiff" the vacuum is. A low $\permittivity$ implies a stiff lattice that transmits force essentially instantly.

\subsection{Characteristic Impedance ($\impedance$)}
The ratio of these two moduli defines the \textbf{Characteristic Impedance} of the universe:
\begin{equation}
    \impedance = \sqrt{\frac{\permeability}{\permittivity}} \approx 376.73 \, \Omega
\end{equation}
This is the "acoustic impedance" of the vacuum. It dictates the efficiency of energy transfer. The fact that $\impedance$ is finite (and not zero) is the only reason electromagnetic waves can propagate at all.