\section{The Macroscopic Moduli of the Void}
\label{sec:moduli}

In standard physics, $\mu_0$ and $\epsilon_0$ are treated as disembodied, continuous field properties. In Vacuum Engineering, they are strictly defined as the \textbf{Constitutive Moduli} of the discrete mechanical substrate, bridging the discrete finite-element parameters ($L_{node}, C_{EM}$) to continuous fields.

\subsection{Magnetic Permeability ($\mu_0$) as Linear Mass Density}
The magnetic constant $\mu_0 \approx 1.256 \times 10^{-6} \text{ H/m}$ represents the \textbf{Inductive Inertia} of the lattice nodes distributed over the fundamental length: $\mu_0 \equiv L_{node}/l_{node}$. 

Mechanically, this is analogous to continuous fluid inertia. We can rigorously prove its physical identity using the Topological Conversion Constant ($\xi_{topo} \equiv e/l_{node}$). Since Inductance maps strictly to Mass scaled by the topology ($[H] \equiv \xi_{topo}^{-2} [kg]$):
\begin{equation}
    [\mu_0] = \frac{\text{H}}{\text{m}} \xrightarrow{\xi_{topo}} \mathbf{\frac{1}{\xi_{topo}^2} \left[ \frac{\text{kg}}{\text{m}} \right]}
\end{equation}
This mathematically proves that $\mu_0$ is the exact mechanical Linear Mass Density of the vacuum lattice, scaling directly with the inverse square of the topological dislocation. It determines how "heavy" the vacuum is, forming the continuous physical origin of inertial lag.

\subsection{Electric Permittivity ($\epsilon_0$) as Capacitive Compliance}
The electric constant $\epsilon_0 \approx 8.854 \times 10^{-12} \text{ F/m}$ represents the \textbf{Capacitive Compliance} of the discrete lattice edges distributed over the length: $\epsilon_0 \equiv C_{EM}/l_{node}$. 

Applying the Topological Constant, Capacitance maps directly to mechanical compliance (inverse stiffness):
\begin{equation}
    [\epsilon_0] = \frac{\text{F}}{\text{m}} = \frac{\text{C}^2}{\text{N}\cdot\text{m}^2} \xrightarrow{\xi_{topo}} \frac{(\xi_{topo} \text{ m})^2}{\text{N}\cdot\text{m}^2} = \mathbf{\xi_{topo}^2 \left[ \frac{1}{\text{N}} \right]}
\end{equation}
This proves that $\epsilon_0$ is the exact physical inverse of the manifold's string tension ($T$), scaled by $\xi_{topo}^2$. It quantifies how much the vacuum lattice yields under a unitary mechanical force.

\subsection{Characteristic Impedance ($Z_0$) and Slew Rate ($c$)}
The ratio of these two continuum moduli natively cancels the length scale, yielding the exact \textbf{Characteristic Impedance} of the discrete geometry ($Z_0 = \sqrt{\mu_0/\epsilon_0} \approx 376.73 \, \Omega$). Applying the dimensional reduction yields $Z_0 \equiv \xi_{topo}^{-2} \, \text{kg/s}$, proving electromagnetic impedance is physically identical to mechanical acoustic drag. 

Consequently, the speed of light emerges not as a relativistic postulate, but as the strict \textbf{Global Slew Rate} of the underlying distributed hardware limits. By evaluating the discrete propagation delay of the finite-element transmission line, the continuous wave speed perfectly emerges:
\begin{equation}
    c = \frac{l_{node}}{\sqrt{L_{node} C_{EM}}} = \frac{l_{node}}{\sqrt{(\mu_0 l_{node})(\epsilon_0 l_{node})}} = \mathbf{\frac{1}{\sqrt{\mu_0 \epsilon_0}}}
\end{equation}