\section{Dielectric Saturation Limit}
\label{sec:saturation}

Every physical material has a breakdown voltage. The vacuum is no exception. We define the \textbf{Breakdown Voltage} ($V_0$) as the saturation limit of the lattice.

\subsection{The Schwinger Limit}
Standard QED predicts that at an electric field strength of $E_{crit} \approx 1.32 \times 10^{18}$ V/m, the vacuum "boils," spontaneously generating electron-positron pairs. In Vacuum Engineering, this is the point where the capacitive edges of the graph ($E$) rupture.

\subsection{Non-Linear Response}
Below this limit, the vacuum acts as a linear medium (Hooke's Law). Near this limit, the stress-strain curve becomes non-linear.
\begin{equation}
    D = \permittivity E + \chi^{(3)} E^3 + \dots
\end{equation}
This non-linearity is crucial for:
\begin{enumerate}
    \item \textbf{Particle Genesis:} Creating stable topological knots (Matter).
    \item \textbf{Black Holes:} Regions where the lattice is stressed to maximal density.
\end{enumerate}
We postulate that the \textbf{Saturation Energy} ($E_{\mathrm{sat}}$) is simply the total energy storage capacity of a single lattice cell before dielectric breakdown occurs.

\section{The Breakdown Limit ($V_0$): A Geometric Definition}
\label{sec:breakdown_voltage}

To avoid circular definitions, we do not calibrate $V_0$ to the Planck Energy. Instead, we define it via the \textbf{Maximum Topological Packing Density}.

Consider a single lattice node with capacitance $C_0$. The maximum charge $Q_{max}$ it can hold is limited not by an arbitrary constant, but by the \textbf{Singularity Condition}:
\begin{equation}
Q_{max} = \oint_{S^2} D \cdot dA \quad \text{s.t.} \quad U_{field} = E_{mass}
\end{equation}
The breakdown voltage $V_0$ is the potential at which the electrostatic energy of the node's field equals the mass-energy required to create a new node (pair production).
\begin{equation}
\frac{1}{2} C_0 V_0^2 = 2 m_{node} c^2
\end{equation}
Since $m_{node}$ is defined by the lattice inertia $\mu_0 l_0$, this limit is a self-contained hardware specification:
\begin{equation}
V_0 = 2c \sqrt{\frac{\mu_0}{\epsilon_0}} = 2c Z_0 \approx 753 \text{ Volts} \times \text{ (Scaling Factor } N_{scale})
\end{equation}
This derivation anchors the breakdown limit to the characteristic impedance $Z_0$ and the speed of light $c$, independent of Planck's constant $\hbar$.