\section{Resolving Prior Quantum Anomalies via SCA}

By defining the vacuum as an LC network and treating continuous fields as macroscopic network dynamics, Spacetime Circuit Analysis (SCA) naturally demystifies the most famous "spooky" paradoxes of 20th-century physics.

\subsection{The Aharonov-Bohm Effect (Irrotational Advection)}
In 1959, Aharonov and Bohm proved that an electron passing around a perfectly shielded magnetic field still experiences a quantum phase shift. Standard physics categorizes this as non-local "action at a distance" because the magnetic field ($\mathbf{B}$) is zero outside the shield.

In the AVE framework, the Vector Potential ($\mathbf{A}$) is the continuous momentum flow of the spatial network. Even if the network has zero vorticity ($\mathbf{B} = \nabla \times \mathbf{A} = 0$), the network can still possess a steady, irrotational bulk flow ($\mathbf{A} \neq 0$). 
Because Magnetic Flux is exactly mechanical momentum ($\Phi_{mag} \equiv \xi_{topo}^{-1} p_{vac}$), the Aharonov-Bohm phase shift ($\Delta \phi = \frac{e}{\hbar} \Phi_{mag}$) evaluates flawlessly to classical network advection. The particle's pilot wave isn't experiencing non-local magic; it is simply a wave being physically carried downstream by the invisible, irrotational river current of the vacuum network.

\subsection{The Casimir Effect (LC Mode Exclusion)}
In 1948, Hendrik Casimir proved that two uncharged plates placed nanometers apart will attract each other due to "zero-point vacuum fluctuations."

In SCA, empty space is a cascaded LC transmission line. Placing two conductive plates close together physically short-circuits any discrete LC nodes with a resonant wavelength larger than the physical gap. By mechanically excluding these long-wavelength inductive resonance modes, the total stored reactive zero-point energy of the local vacuum drops. 
The spatial gradient of this missing energy creates a pure, mechanical Ponderomotive force pulling the plates together. The Casimir effect is the literal macroscopic proof that the vacuum is a quantized LC network!