\section{Constitutive Circuit Models for Vacuum Non-Linearities}
Standard circuit simulators rely on ideal, linear RLC components. However, physical topological condensates exhibit highly non-linear behaviors under extreme mechanical stress. By applying the Topo-Kinematic identity, we can construct the exact non-linear equivalent circuit components of the spatial metric.

\subsection{1. The Metric Varactor (Modeling Dielectric Yield)}
As defined by Axiom 4, the effective compliance (capacitance) of the spatial substrate is structurally bounded by the absolute classical dielectric saturation limit ($V_{crit} \equiv \alpha$). As the local topological potential approaches this limit, the effective capacitance increases non-linearly. This structurally mirrors a Voltage-Dependent Varactor Diode, rigorously yielding the 4th-order bounding required to satisfy standard optical Kerr effect limits:
\begin{equation}
C_{vac}(V) = \frac{C_0}{\sqrt{1 - (V/V_{crit})^4}}
\end{equation}

\subsection{2. The Relativistic Inductor (Lorentz Saturation)}
Because inertia maps to spatial inductance, and velocity maps to spatial current, the phenomenon of Special Relativity is identically modeled in SCA as a non-linear inductor. The effective inductance saturates as the macroscopic current approaches the fundamental hardware propagation limit ($I_{max} = \xi_{topo} c$):
\begin{equation}
L_{vac}(I) = \frac{L_0}{\sqrt{1 - (I/I_{max})^2}}
\end{equation}
This provides the mechanical rationale for why standard SPICE simulators natively cannot push current (matter) past $c$; the localized inductive drag asymptotes to infinity, mirroring the aerodynamic Prandtl-Glauert singularity.

\subsection{3. The Viscoelastic TVS Zener Diode (Bingham Transition)}
In a Bingham Plastic continuum, viscosity yields strictly when subjected to extreme shear stress ($\tau > \tau_{yield}$). Because macroscopic shear stress is proportional to mechanical force, vacuum liquefaction must act as a Voltage-Driven Breakdown. The vacuum substrate acts electrically as a Transient Voltage Suppression (TVS) Zener Diode. Below $V_{yield}$, it acts as a highly resistive solid (kinematically gripping matter). Above $V_{yield}$, it enters avalanche breakdown, allowing frictionless superfluid slip.

\subsection{4. The Vacuum Memristor (Thixotropic Hysteresis)}
Because the Bingham-plastic transition of the $\mathcal{M}_A$ condensate requires a finite geometric relaxation time ($\tau_{macro} \approx L/c$) to physically liquefy, the vacuum cannot alter its fluidic resistance instantaneously. Its state is rigidly dependent on the historical integral of the stress applied to it. Consequently, the physical vacuum completes the fundamental electronic quartet by acting as a \textbf{Macroscopic Memristor}, exhibiting a strict pinched hysteresis loop when subjected to high-frequency AC topological stress.