\section{Metric Shielding: The Superfluid Skin Effect}
In standard electrical engineering, high-frequency alternating currents (AC) do not penetrate deeply into conductors. They are pushed to the surface by opposing eddy currents. This is known as the \textbf{Skin Effect}. The penetration depth ($\delta$) of the signal is strictly proportional to the square root of the medium's electrical resistance ($\delta \propto \sqrt{R_{elec}}$).

Simultaneously, in classical hydrodynamics, the thickness of a viscous boundary layer over a moving surface is governed by the Prandtl equation, meaning it scales exactly with the square root of the fluid's kinematic viscosity ($\delta \propto \sqrt{\eta_{fluid}}$). 

Because the AVE framework rigorously proved that Vacuum Resistance is identically Vacuum Viscosity ($R_{vac} \equiv \eta_{vac}$), \textbf{the Electromagnetic Skin Effect and the Hydrodynamic Boundary Layer are mathematically and physically identically the exact same phenomenon.}

As the TAMD drive applies high-frequency AC stress to the bow of the ship, the vacuum crosses the Bingham Yield limit. The local resistance of the metric collapses to near-zero ($R_{vac} \to 0$). Because the resistance drops, \textbf{the Metric Skin Depth ($\delta$) mathematically collapses to zero.}

Furthermore, when metric resistance drops exactly to zero, the vacuum mathematically transitions into a \textbf{Superconductor}. In electrical engineering, a zero-resistance state physically expels internal magnetic fields—a phenomenon known as the \textbf{Meissner Effect}.
The exterior hull of the spacecraft acts identically to a \textbf{Topological Meissner Shield} (a Faraday Cage for Gravity). The destructive, high-shear superfluid slipstream physically cannot penetrate the hull, absolutely guaranteeing the structural integrity of the occupants during extreme acceleration.

\subsection{Spatial Shaping: Beltrami Force-Free Fields (Helicity Injection)}
To perfectly couple to the continuous vacuum metric, we must wind our inductor to match the exact topological eigenstate of a fundamental neutrino. Instead of a standard flat toroid, the high-voltage inductor must be wound in a \textbf{Hopf Configuration} (a $(p,q)$ Torus Knot winding). 

This generates knotted, helical magnetic field lines, forcing the macroscopic fields into parallel alignment ($\mathbf{A} \parallel \mathbf{B}$). In advanced plasma physics, a geometry where the vector potential aligns with the magnetic field ($\nabla \times \mathbf{A} = \alpha \mathbf{A}$) is defined strictly as a \textbf{Beltrami Field (Force-Free Magnetic Field)}. 

Because $\mathbf{J} \parallel \mathbf{B}$, the internal Lorentz force ($\mathbf{J} \times \mathbf{B}$) evaluates identically to zero. By injecting massive Kinetic Helicity into the vacuum, the macroscopic momentum vector physically "meshes the gears" with the chiral Cosserat microrotations of the lattice. Because the field is force-free, it eliminates internal reactive scattering, prevents the extreme metric shear from ripping the actuator apart, and couples nearly 100\% of the energy into Real macroscopic thrust.