\section{Black Holes and the Death of the Rubber Sheet}

For over a century, General Relativity has illustrated gravitation via the abstract ``Rubber Sheet'' metaphor, dictating that inside a Black Hole, this continuous sheet stretches infinitely downward to a singular point of infinite density. In engineering, no physical material stretches infinitely; every substrate possesses an ultimate tensile strength. 

\subsection{The Dielectric Snap}

As established in Chapter 1, the hardware is strictly bounded by the Schwinger Yield Energy Density ($u_{sat} \approx 10^{25}$ J/m$^3$). As matter aggregates, the inductive strain on the local nodes increases. As we approach the Event Horizon of a black hole, the tensor strain on the discrete edges reaches this absolute thermodynamic limit.

At the exact mathematical radius of the Event Horizon, the rubber sheet physically snaps.

The compressive stress shatters the Delaunay triangulation of the graph. The discrete nodes undergo a sudden thermodynamic phase transition (melting), reverting back into the unstructured Pre-Geometric continuous fluid. There is no infinite funnel; there is only a flat, unstructured thermodynamic plasma floor.

\subsection{Resolution of the Information Paradox}

This localized phase transition provides the definitive mechanical resolution to the Black Hole Information Paradox.

In DCVE, fermions and baryons are stable topological knots tied exclusively out of the discrete lattice edges. Because the melted interior of the event horizon lacks a discrete graphical structure, it physically cannot support phase transport or topological defects. When knotted matter crosses the Event Horizon, the underlying physical lattice supporting the knot literally ceases to exist.

The knot is not crushed into a singularity; it is instantly unraveled. The raw mass-energy of the knot is perfectly conserved and added to the latent heat of the melt, but the geometric information (the crossing topology) is physically and permanently erased. The paradox is resolved because the physical structural canvas upon which the quantum information was encoded is thermodynamically destroyed. Black holes are the cosmic recycling vats of the spacetime engine, melting exhausted discrete space back into the quantum continuum to fuel further genesis.