\documentclass[11pt, titlepage, oneside]{book}

% --- Core Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1.1in}
\usepackage{amsmath, amssymb, physics}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{cite}
\usepackage{listings}
\usepackage{booktabs} % For professional tables
\usepackage{titlesec} % For professional chapter titles

% --- Path to Figures ---
\graphicspath{{assets/}}

% --- Advanced Hyperlink Setup ---
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue,
    pdftitle={The Discrete Vacuum Substrate},
    breaklinks=true
}

% --- Code Listing Configuration (Graduate Style) ---
\definecolor{backcolour}{rgb}{0.96,0.96,0.94}
\lstset{
    backgroundcolor=\color{backcolour},
    basicstyle=\ttfamily\footnotesize,
    breaklines=true,
    captionpos=b,
    numbers=left,
    numberstyle=\tiny\color{gray},
    keywordstyle=\color{blue},
    commentstyle=\color{green!50!black},
    frame=single
}

% --- Custom Definitions ---
\newcommand{\LCT}{\textit{Lattice Constitutive Theory}}

% --- Document Metadata ---
\title{
    \Huge \textbf{The Discrete Vacuum Substrate} \\
    \Large \textit{A Hydrodynamic Approach to Unified Field Theory}
}
\author{Grant Lindblom}
\date{February 2026 Edition}

% --- Main Content ---
\begin{document}

\frontmatter
\maketitle

\section*{Preface: A Multidisciplinary Foundation}
This text represents a shift from the geometric abstraction of the 20th century toward a constitutive, hardware-oriented understanding of the cosmos. By merging Electrical Engineering (RF Impedance), Fluid Mechanics (Superfluidity), and Theoretical Physics (NLSE), we provide a unified framework for the graduate-level researcher.

\subsection*{How to Use This Book}
This textbook is designed to be accessible to physicists, engineers, and mathematicians alike. However, each field uses different dialects to describe the same phenomena. To bridge this gap:

\begin{itemize}
    \item \textbf{The Glossary:} The frontmatter contains a comprehensive \textbf{Translation Matrix}. We strongly recommend reviewing this first. It maps new LCT terms (like "Vacuum Impedance") to their familiar analogs (like "Refractive Index" or "Characteristic Impedance").
    \item \textbf{Bridge the Gap:} At the end of each chapter, you will find a "Bridge the Gap" section. This explicitly translates the chapter's derivation into the language of your specific field.
    \item \textbf{Computational Verification:} Physics is not a spectator sport. The associated GitHub repository contains the Python simulations referenced in the "Computational Module" sections. We encourage you to run these scripts to verify the theory for yourself.
\end{itemize}

\tableofcontents

% --- Include the Glossary ---
\input{frontmatter/glossary}

\mainmatter

% --- Chapter 1: Foundations (Old Paper 1) ---
\chapter{The Unified Action Principle}
\input{chapters/chapter1}

% --- Chapter 2: Hardware (Old Paper 2) ---
\chapter{Vacuum Impedance and Transmission Lines}
\input{chapters/chapter2}

% --- Chapter 3: Micro-Dynamics (Old Paper 3) ---
\chapter{Vortex Topology and Emergent Quantum Mechanics}
\input{chapters/chapter3}

% --- Chapter 4: Cosmology (Old Paper 4) ---
\chapter{The Entangled Substrate and Cosmic Genesis}
\input{chapters/chapter4}

% --- Chapter 5: Phase Transitions (Old Paper 5) ---
\chapter{The Thermodynamic Vacuum and Decoherence}
\input{chapters/chapter5}

% --- Chapter 6: Anomalies (Old Paper 6) ---
\chapter{Cosmological Impedance Evolution and Anomalies}
\input{chapters/chapter6}
\appendix
\input{chapters/appendix_a}
\input{chapters/appendix_b}

\backmatter
\begin{thebibliography}{99}
    \bibitem{volovik} Volovik, G. E. (2003). \textit{The Universe in a Helium Droplet}.
    \bibitem{couder} Couder, Y., \& Fort, E. (2006). Single-particle diffraction and interference at a macroscopic scale. \textit{Physical Review Letters}, 97(15), 154101.
    \bibitem{bell} Bell, J. S. (1964). On the Einstein Podolsky Rosen paradox. \textit{Physics Physique Feniz}, 1(3), 195.
    \bibitem{hawking} Hawking, S. W. (1975). Particle creation by black holes. \textit{Communications in Mathematical Physics}, 43(3), 199-220.
    \bibitem{kibble} Kibble, T. W. (1976). Topology of cosmic domains and strings. \textit{Journal of Physics A: Mathematical and General}, 9(8), 1387.
\end{thebibliography}

\end{document}