% 07_neutrino_sector.tex
\chapter{The Neutrino Sector: Chiral Unknots}
\label{ch:neutrino_sector}

Neutrinos are the most abundant massive particles in the universe, yet they interact extraordinarily weakly and possess rest masses significantly smaller than the electron. In the AVE framework, the neutrino's unique properties are the direct mathematical consequence of its topology: it is a \textbf{Twisted Unknot ($0_1$)}.

\section{Mass Without Charge: The Faddeev-Skyrme Proof}
Because the neutrino is an unknot ($0_1$), it forms a simple closed topological loop. To mathematically satisfy Spin-1/2, it contains a $4\pi$ internal torsional phase twist. However, it possesses strictly \textbf{zero self-crossings} ($C=0$). Therefore, its winding number and electric charge evaluate to exactly zero ($Q_H \equiv 0$).

To rigorously evaluate the neutrino's mass, the Faddeev-Skyrme energy functional is applied using the strictly 4th-order Axiom 4 saturation limit ($\sqrt{1 - (\Delta\phi/\alpha)^4}$). Because the neutrino lacks crossings, it completely lacks a dense topological core. Without a localized crossing to force distinct flux lines into a minimal hardware volume, there is zero flux crowding.

Consequently, the local dielectric phase gradient ($\Delta\phi$) remains negligible. The non-linear dielectric saturation denominator remains safely in the linear regime at precisely $\approx 1.0$.

Significantly, because the non-linear Skyrme tensor explicitly requires orthogonal spatial gradients $(\partial_\mu \mathbf{n} \times \partial_\nu \mathbf{n})^2$, the total absence of physical intersections ensures the gradient vectors never cross. The topological Skyrme term identically vanishes. The mass-energy of the neutrino is bounded entirely by the pure, un-amplified linear kinetic torsional term.

It completely avoids the dielectric saturation capacitance divergence defined in Axiom 4, resulting natively in an ultra-low rest mass. Furthermore, lacking a massive saturated inductive core, it translates longitudinally along the spatial edges without generating macroscopic fluidic drag, which accounts for its extreme penetrative capabilities.

\section{The Chiral Exclusion Principle (Parity Violation)}
The Standard Model exhibits a distinct geometric asymmetry: all experimentally observed neutrinos are strictly left-handed. The AVE framework derives parity violation directly from the microrotational solid-state mechanics of the trace-reversed Cosserat vacuum.

Transverse waves propagating through a structurally chiral lattice exhibit an asymmetric dispersion relation:
\begin{equation}
    \omega^2 = c^2 k^2 \mp \gamma_c k
\end{equation}
Where $\gamma_c$ represents the intrinsic microrotational stiffness.

When a \textbf{left-handed} torsional wave propagates, the sign algebraically matches the intrinsic structural grain of the substrate ($\omega^2 = c^2 k^2 + \gamma_c k$). The frequency squared remains strictly positive, allowing the signal to propagate freely.

However, a \textbf{right-handed} torsional wave mathematically shears \textit{against} the immense microrotational stiffness. At the single-node spatial cutoff ($\ell_{node}$), the $\gamma_c$ restoring torque completely overwhelms the kinetic term:
\begin{equation}
    \omega^2 = c^2 k^2 - \gamma_c k < 0
\end{equation}
The frequency squared is forced strictly negative. In discrete wave mechanics, an imaginary frequency forces the solution to become an \textbf{Evanescent Wave}. The right-handed neutrino is mechanically forbidden from propagating. The Cosserat lattice subjects it to Anderson localization, causing the wave envelope to decay to absolute zero within a single fundamental node length. Parity violation is thus proven to be a strict solid-state mechanical filter.

\section{Neutrino Oscillation: Dispersive Beat Frequencies}
Neutrinos are structurally defined by \textbf{Torsional Harmonics} loaded onto the zero-crossing unknot. The discrete flavors correspond to the quantized number of full internal twists ($T$): Electron ($T=1$), Muon ($T=2$), and Tau ($T=3$).

Because neutrinos possess inductive rest mass, their matter-waves are subjected to an explicit massive dispersion relation ($v_g(k) = c \cos(k \ell_{node}/2)$). Because the $T=1, 2$, and $3$ torsional overtones possess different spatial wavenumbers ($k_i$), they propagate through the discrete Cosserat grid at fractionally different group velocities ($v_g < c$).

Neutrino oscillation is formally modeled not as an abstract state-vector rotation, but as the classical, acoustic \textbf{Beat Frequency} of a multi-harmonic torsional wave packet undergoing microscopic structural dispersion across the fundamental hardware grid.