\section{Axiomatic Dependency and Mathematical Closure}

\subsection{Proving the Absence of Circular Logic}
A common and important question for grand unified frameworks and emergent gravity models is the risk of "syntactic tautology"—where empirical constants are defined in terms of each other in a circular way to balance equations.

To show that the Applied Vacuum Engineering (AVE) framework maintains mathematical closure without phenomenological parameter tuning, we map the Directed Acyclic Graph (DAG) of its derivations.

\textbf{The One-Parameter Foundation:} AVE is a Rigorous One-Parameter Theory. All predictive power derives from exactly two geometric axioms and one empirical calibration:
\begin{enumerate}
    \item \textbf{Axiom 1 (Topo-Kinematic Isomorphism):} Charge is identically equal to spatial dislocation ($[Q] \equiv [L]$).
    \item \textbf{Axiom 2 (Cosserat Elasticity):} The vacuum acts as a Trace-Free Cosserat solid supporting microrotations.
    \item \textbf{Empirical Calibration:} The absolute metric scale of the lattice ($l_{node}$) is anchored by the fundamental fermion (the classical mass-energy limit of the electron). 
\end{enumerate}

\subsection{The Forward-Flow of the Framework}
From these three foundational elements, all physical constants emerge in a forward-flowing sequence:
\begin{itemize}
    \item \textbf{Geometry:} The electron calibration defines the Porosity Ratio ($\alpha \approx 1/137$), which geometrically determines the volumetric packing fraction of the Delaunay graph ($\kappa_V = 8\pi\alpha$).
    \item \textbf{Electromagnetism and Inertia:} Axiom 1 yields the topological conversion constant ($\xi_{topo}$), connecting electrical resistance to the inverse of mechanical inertial drag, and magnetic flux to mechanical momentum.
    \item \textbf{The Weak Force:} The Cosserat requirement (Axiom 2) sets the bulk/shear moduli to $K=2G$. This produces the vacuum Poisson's ratio $\nu_{vac} = 2/7$, which yields the Weak Mixing Angle mass ratio ($m_W / m_Z \approx 0.8819$) without arbitrary symmetry-breaking parameters.
    \item \textbf{Gravity and Cosmology:} The 1D QED tension limit ($T_{EM}$) is scaled by the cosmic hierarchy coupling ($\xi$). Projecting this 1D scalar stress into the 3D bulk metric of General Relativity requires evaluating the Interaction Lagrangian of the trace-reversed stress-energy tensor. This evaluation yields the $1/7$ tensor projection factor from the GR trace-reversal operator and $\nu_{vac}$. This reduction gives Newton's $G$. We note the linear dependency between $G$ and $H_0$; AVE addresses the Hubble Tension by closing the Dirac Constraint Triangle, predicting $H_0 \approx 69.32$ km/s/Mpc from empirical $G$ and local quantum constants.
    \item \textbf{Thermodynamics:} The fixed packing fraction ($\kappa_V$) prevents the lattice from storing excess expansion energy, leading to 100\% efficient ejection of latent heat. This open-system transition yields Stable Phantom Dark Energy ($w_{vac} \approx -1.0001$) bounded from a Big Rip by the Cosmic Microwave Background thermal attractor. 
\end{itemize}

Because information flows outward from geometric topology to macroscopic observables—without feedback loops—the AVE framework is mathematically closed, highly falsifiable, and free of arbitrary hidden variables.