\chapter{Generative Cosmology and the Dark Sector}
\label{ch:cosmology}

\section{Lattice Genesis: The Origin of Metric Expansion}
Standard cosmology relies on the mathematical assumption of ``Metric Expansion''—an empty coordinate geometry stretching arbitrarily. The AVE framework explicitly prohibits stretching a fundamental limit. A discrete lattice cannot stretch macroscopically without catastrophically breaking its Delaunay triangulation. Metric expansion must be fundamentally quantized as the discrete, real-time \textbf{Crystallization} of new topological nodes.

To preserve the invariant spatial density of the hardware globally ($\partial_t \rho_n = 0$), the Eulerian Continuity Equation dictates the discrete generative source term must identically match the macroscopic volumetric expansion divergence ($\Gamma_{genesis} = \rho_n \nabla \cdot \mathbf{v}$). The rate of node generation required to maintain the baseline spatial density evaluates directly to the Hubble parameter ($dN/dt = H_0 N(t)$). Integrating this continuous generative rate mathematically yields the exact exponential scale-factor growth of the universe:
\begin{equation}
    a(t) = e^{H_0 t}
\end{equation}

\section{Dark Energy: The Stable Phantom Derivation}
During Lattice Genesis, the phase transition continuously expels a Latent Heat of Fusion ($\rho_{latent} dV$) into the ambient photon gas (CMB). By the First Law of Thermodynamics, to physically fund the internal energy of the newly created spatial volume ($\rho_{vac}$) while simultaneously expelling this latent heat, the total macroscopic mechanical pressure ($P_{tot}$) of the vacuum must be strictly negative.
\begin{equation}
    -P_{tot} dV = \rho_{vac} dV + \rho_{latent} dV \implies P_{tot} = -(\rho_{vac} + \rho_{latent})
\end{equation} 

Calculating the equation of state natively derives \textbf{Phantom Dark Energy}:
\begin{equation}
    w_{vac} = \frac{P_{tot}}{\rho_{vac}} = \mathbf{-1 - \frac{\rho_{latent}}{\rho_{vac}} < -1}
\end{equation}
Standard Phantom Energy models generate a runaway "Big Rip." In AVE, because the topological density is rigidly locked by the QED packing fraction ($\kappa_V = 8\pi\alpha$), excess phantom work cannot be stored in the vacuum. It is 100\% ejected as latent heat, permanently averting the Big Rip and strictly bounding Dark Energy at $w_{vac} \approx -1.0001$.

\section{The CMB as an Asymptotic Thermal Attractor}
The continuous injection of latent heat into the CMB dynamically forms a permanent asymptotic thermal floor. Competing against standard adiabatic expansion cooling ($a^{-4}$), the thermodynamic history of the universe perfectly integrates to:
\begin{equation}
    u_{rad}(a) = U_{hot} \, a^{-4} + \mathbf{\frac{3}{4} \rho_{latent}}
\end{equation}
The universe cools precisely according to the Hot Big Bang model, but as $a \to \infty$, it smoothly bottoms out at the fundamental Unruh-Hawking limit ($T_U \sim 10^{-30}$ K). The universe will never freeze to absolute zero, forever resolving the Heat Death paradox.

\section{Black Holes and the Dielectric Snap}
No physical substrate stretches infinitely to a singularity. As matter aggregates into a hyper-dense core, the macroscopic inductive refractive strain ($n_\perp = 1 + 2GM/rc^2$) increases. At the exact mathematical radius of the Event Horizon, the continuous tensor strain on the discrete edges violently reaches the Axiom 4 Dielectric Saturation limit ($\alpha$). 

The spatial rubber sheet physically \textbf{snaps}. The discrete nodes undergo a sudden thermodynamic phase transition, melting back into the unstructured, pre-geometric continuous plasma. There is no singularity; there is only a flat thermodynamic floor.

Because topological particles (knots) fundamentally require the discrete lattice edges to maintain their invariants, crossing the Event Horizon destroys the lattice canvas beneath them. The knots literally unspool. The mass-energy is conserved as latent heat, but the geometric quantum information is physically, mathematically, and permanently erased, perfectly resolving the Black Hole Information Paradox.