\section{Chirality and Antimatter}

Because the $\mathcal{M}_A$ vacuum is a trace-reversed Cosserat solid supporting intrinsic microrotations, it possesses a preferred topological grain, naturally breaking the absolute symmetry between Left and Right. Electric charge polarity is defined structurally as \textbf{Topological Twist Direction} (Left-Handed vs. Right-Handed helicity).

An Electron ($e^-$) is a Right-handed $3_1$ Trefoil. A Positron ($e^+$) is physically identical in every dimension, except it is woven as a Left-handed $3_1$ Trefoil. 

\subsection{Annihilation: The Dielectric Snap}
By Mazur's Theorem in topology, the connected sum of a left-handed knot and a right-handed knot produces a composite "Square Knot," not a flat unknot. In a continuous mathematical manifold, matter-antimatter annihilation is topologically impossible because strings cannot pass through each other.

The AVE framework natively resolves this paradox seamlessly via the \textbf{Dielectric Reconnection Postulate} (Axiom 4). When opposite chiral knots (e.g., an Electron and Positron) collide, their combined localized inductive strain instantly exceeds the absolute Vacuum Saturation Limit ($\Delta\phi > \alpha$). 

At this exact threshold, the continuous field equations physically break down. The discrete, finite-element edges of the manifold physically "snap" and undergo Dielectric Rupture. In this transient, super-critical melted state, the graph is momentarily severed, entirely disabling the topological invariants that protect the knots. The trapped inductive energy violently unwinds into pure, un-knotted transverse vector waves (Gamma-Ray Photons) as the discrete substrate instantly cools and re-triangulates to a relaxed ground state behind them.