\chapter*{Glossary and Acronyms}
\addcontentsline{toc}{chapter}{Glossary and Acronyms}

\section*{G.1 Core LCT Acronyms}
The following acronyms facilitate the translation of vacuum hardware dynamics into observable physics.

\begin{table}[h!]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Acronym} & \textbf{Full Term} & \textbf{LCT Definition} \\ \hline
\textbf{B-EMF} & Back-Electromotive Force & Mechanical precursor to \textbf{Inertia}; resistance to flux change. \\ \hline
\textbf{FDTD} & Finite-Difference Time-Domain & Numerical method used to solve discrete vacuum equations. \\ \hline
\textbf{GL} & Ginzburg-Landau & Relaxation equation for modeling topological assembly. \\ \hline
\textbf{LCT} & Lindblom Coupling Theory & Hardware-oriented unified field theory modeling the vacuum. \\ \hline
\textbf{TVS} & Transient Voltage Suppressor & Analogy for the \textbf{Weak Interaction} and its directional clamping. \\ \hline
\textbf{ZPE} & Zero-Point Energy & Oscillating tension of the vacuum lattice ground state. \\ \hline
\textbf{TDGL} & Time-Dependent Ginzburg-Landau & Equation governing the \textbf{Global Quench} and phase transitions. \\ \hline
\end{tabular}
\caption{LCT specialized acronyms and engineering definitions.}
\end{table}

\section*{G.2 Exhaustive Glossary of Terms}

\subsection*{A}
\begin{itemize}
    \item \textbf{Abrikosov Lattice}: A quantized vortex lattice formed in the superfluid vacuum. In LCT, the elastic stiffness of this lattice is the mechanical origin of \textbf{Dark Matter}.
    \item \textbf{Acoustic Metric}: A fluid-mechanical model recovering the Schwarzschild metric via a flowing medium.
    \item \textbf{Amorphous Topological Glass}: The hardware state of the vacuum; a disordered Voronoi lattice formed during the \textbf{Global Quench}.
\end{itemize}

\subsection*{B}
\begin{itemize}
    \item \textbf{Bandwidth Saturation}: The state where a lattice node reaches its maximum update frequency ($\omega_{\text{cutoff}}$); the origin of \textbf{Rest Mass}.
    \item \textbf{Bohr Radius}: The stable orbital distance where electron wake resonance balances Coulomb attraction.
    \item \textbf{Bouncing Soliton}: A particle modeled as a localized walker surfing the gradient of its own memory field.
\end{itemize}

\subsection*{C}
\begin{itemize}
    \item \textbf{Casimir Effect}: Modeled as a \textbf{Band-Stop Filter} excluding noise modes from a cavity, creating a pressure deficit.
    \item \textbf{Characteristic Impedance ($Z_0$)}: The ratio of vacuum voltage to current ($\approx 376.73\,\Omega$), derived from nodal inductance and capacitance.
    \item \textbf{Chirality Filter}: The mechanism where the lattice reflects right-handed helical signals, explaining \textbf{Parity Violation}.
    \item \textbf{Compton Frequency ($\omega_c$)}: The natural oscillation frequency of a particle soliton on the hardware lattice.
\end{itemize}

\subsection*{D}
\begin{itemize}
    \item \textbf{Dark Energy}: The **Latent Heat** released by the vacuum substrate as it crystallizes and releases potential energy (work).
    \item \textbf{Dark Matter}: The rotational stiffness ($k$) of the vacuum's Abrikosov vortex lattice, resisting galactic shear.
\end{itemize}

\subsection*{E}
\begin{itemize}
    \item \textbf{Event Horizon}: A boundary of **Total Internal Reflection** where the local refractive index $n \to \infty$.
\end{itemize}

\subsection*{G}
\begin{itemize}
    \item \textbf{Global Quench}: The primordial phase transition where the fluid vacuum "froze" into its current amorphous glass state.
\end{itemize}

\subsection*{H}
\begin{itemize}
    \item \textbf{Hubble Pulse}: A late-time acceleration in expansion caused by a secondary vacuum crystallization event ($z \approx 10$).
\end{itemize}

\subsection*{I}
\begin{itemize}
    \item \textbf{Impedance Clamping}: Non-linear mechanical response where a signal (e.g., a right-handed neutrino) encounters effectively infinite impedance.
\end{itemize}

\subsection*{K}
\begin{itemize}
    \item \textbf{Kibble-Zurek Mechanism}: The process trapping topological defects (matter) at domain boundaries during a vacuum \textbf{Quench}.
\end{itemize}

\subsection*{L}
\begin{itemize}
    \item \textbf{Lattice Inductance ($L$)}: The inertial component of the vacuum resisting flux changes ($\mu_0$).
    \item \textbf{Lattice Capacitance ($C$)}: The elastic component of the vacuum storing potential energy via strain ($\epsilon_0$).
    \item \textbf{Lindblom Dispersion Relation}: Defines the drop in propagation speed as signal energy saturates hardware bandwidth ($v_g \to 0$ as $\omega \to \omega_{cut}$).
\end{itemize}

\subsection*{M}
\begin{itemize}
    \item \textbf{Madelung Transformation}: A mapping revealing the Schrödinger equation as the motion of a classical superfluid with internal pressure.
    \item \textbf{Metric Strain ($\epsilon$)}: The physical stretching or compression of vacuum nodes, creating a refractive index gradient (Gravity).
\end{itemize}

\subsection*{N}
\begin{itemize}
    \item \textbf{Nodal Jitter}: The high-frequency background noise of the amorphous lattice, identified as the source of **Heisenberg Uncertainty**.
\end{itemize}

\subsection*{P}
\begin{itemize}
    \item \textbf{Phase Bridge}: A high-tension flux tube connecting entangled topological defects; the mechanism for **Confinement** and **Non-Locality**.
    \item \textbf{Pilot Wave}: The standing-wave "memory field" guiding a particle soliton through interference patterns.
    \item \textbf{Proton}: A stable **Trefoil Knot** in the vacuum phase field, composed of three entangled singularities.
\end{itemize}

\subsection*{Q}
\begin{itemize}
    \item \textbf{Quantum Potential ($Q$)}: The internal pressure of the vacuum fluid, derived from the spatial derivative of the density amplitude.
\end{itemize}

\subsection*{S}
\begin{itemize}
    \item \textbf{Schwinger Limit}: The dielectric breakdown threshold of the vacuum substrate ($\approx 10^{18}$ V/m).
    \item \textbf{Slew Rate Limit}: The maximum frequency at which a lattice node can update, defining the global speed limit $c$.
\end{itemize}

\subsection*{T}
\begin{itemize}
    \item \textbf{Topological Defect}: A stable vortex or knot in the vacuum phase field, identified as a discrete particle (electron/quark).
\end{itemize}

\subsection*{V}
\begin{itemize}
    \item \textbf{Vacuum Stiffness}: The elastic resistance of the superfluid condensate to rotation, scaling linearly with radius.
\end{itemize}

\subsection*{W}
\begin{itemize}
    \item \textbf{Weinberg Angle ($\theta_W$)}: A thermal-mechanical property derived from the lattice's **Directional Bias** and effective temperature ($kT_{eff}$).
\end{itemize}