% --- Nomenclature and Fundamental Constants ---
\chapter*{Nomenclature and Fundamental Constants}
\addcontentsline{toc}{chapter}{Nomenclature and Fundamental Constants}

\section*{Universal Hardware Constants}
The following constants define the constitutive properties of the vacuum substrate.

\begin{table}[h]
    \centering
    \begin{tabular}{|l|l|l|l|}
    \hline
    Symbol & Name & Value (LCT) & Physical Equivalent \\
    \hline
    $L$ & Lattice Inductance & $\approx 1.2566 \times 10^{-6}$ H/m & $\mu_0$ (Vacuum Permeability) \\
    $C$ & Lattice Capacitance & $\approx 8.8542 \times 10^{-12}$ F/m & $\epsilon_0$ (Vacuum Permittivity) \\
    $Z_0$ & Characteristic Impedance & $\approx 376.73\,\Omega$ & $\sqrt{L/C}$ \\
    $\Delta x$ & Lattice Pitch & $l_P \approx 1.616 \times 10^{-35}$ m & Discrete nodal spacing \\
    $\omega_{\text{cutoff}}$ & Cutoff Frequency & $2 / \sqrt{LC}$ & Nyquist/Slew limit \\
    \hline
    \end{tabular}
    \caption{Primary hardware variables of the Lindblom Coupling Theory.}
\end{table}

\section*{Emergent Tensors and Variables}
These variables describe the behavior of signals and defects within the lattice.

\begin{itemize}
    \item \textbf{$\epsilon_{\mu\nu}$ (Metric Strain Tensor)}: Represents the physical displacement of lattice nodes, recasting GR curvature as mechanical strain.
    \item \textbf{$Q$ (Quantum Potential)}: Identifies the internal vacuum pressure gradient that guides pilot-wave trajectories.
    \item \textbf{$v_g$ (Group Velocity)}: The propagation speed of energy, which vanishes as signal frequency approaches $\omega_{\text{cutoff}}$.
    \item \textbf{$n$ (Topological Winding Number)}: An integer representing the "twist" of a vortex, identified as electric charge.
    \item \textbf{$Z_{\text{eff}}$ (Effective Impedance)}: The directional impedance encountered by helical pulses, governing the Weak Interaction.
    \item \textbf{$\beta$ (Strain Coefficient)}: A dimensionless factor governing the scaling of metric strain from effective mass, $\epsilon = \beta \frac{m_{\text{eff}}}{m_{\text{Pl}}}$.
\end{itemize}

\section*{Acronyms}
\begin{itemize}
    \item \textbf{B-EMF}: Back-Electromotive Force (Mechanical Inertia).
    \item \textbf{FDTD}: Finite-Difference Time-Domain (Numerical Verification Method).
    \item \textbf{LCT}: Lindblom Coupling Theory.
    \item \textbf{TVS}: Transient Voltage Suppressor (Weak Force Analogy).
\end{itemize}