% 04_physics_engine_architecture.tex
% Appendix: Physics Engine Source Architecture
%
% Documents the three-tier structure of the AVE computational engine,
% maps every module to its axiom-chain entry point, and provides the
% complete function-level API reference.

\chapter{Physics Engine Architecture}
\label{ch:engine_architecture}

The computational physics engine (\texttt{src/ave/}) implements
the AVE framework as executable mathematics.  Every numerical
result in this series---from the fine-structure constant to galactic
rotation curves---is produced by code paths traceable to the four
axioms through the architecture documented below.

\section{Design Principles}

\begin{enumerate}
    \item \textbf{Single source of truth.}  The three universal operators
          ($Z$, $\sigma$, $\Gamma$) are implemented \emph{once} in
          \texttt{scale\_invariant.py}.  No domain module re-derives them.
    \item \textbf{Scale invariance by construction.}  Domain modules
          provide constitutive analogs ($\varepsilon$, $\mu$) only;
          all impedance/saturation/reflection computations delegate
          upward to the universal operators.
    \item \textbf{Axiom traceability.}  Every derived constant and
          function documents its derivation path back to Axioms~1--4.
\end{enumerate}


\section{Three-Tier Architecture}

\begin{figure}[H]
\centering
\begin{verbatim}
Tier 1: CORE (never duplicated)
|-- core/constants.py         All derived constants (Z_0, V_snap, ...)
|-- axioms/scale_invariant.py Z, S, Gamma, T, eps_eff, mu_eff, c_eff, Z_eff

Tier 2: DOMAIN ADAPTERS (thin wrappers providing eps/mu analogs)
|-- gravity/                  n(r), Schwarzschild, heliospheric profiles
|-- plasma/                   omega_p, Drude, skin depth, Meissner
|-- geophysics/               PREM layers, K/G -> eps/mu mapping
|-- fluids/                   H-bond LC model, water density
|-- topological/              Skyrme, Borromean, Cosserat tensors
|-- mechanics/                Refractive strain, mutual inductance

Tier 3: SOLVERS (consume Tiers 1+2, never re-derive operators)
|-- core/fdtd_3d.py           3D nonlinear FDTD engine
|-- solvers/bond_energy_solver     1D FDTD for nuclear bond E(d) curves
|-- solvers/fdtd_lc_network        1D macroscopic gravity FDTD
|-- solvers/protein_bond_constants Backbone derivation chain + data
\end{verbatim}
\caption{Three-tier architecture enforcing scale invariance.
Every computation flows downward; no tier re-derives operators
from a higher tier.}
\label{fig:engine_tiers}
\end{figure}


\section{Tier 1: Core Operators}
\label{sec:tier1_core}

\subsection{\texttt{core/constants.py} --- Derived Constants}

All physical constants derive from four measured inputs
($\hbar$, $c$, $e$, $m_e$) plus the four axioms.
Table~\ref{tab:engine_constants} lists the key derived quantities.

\begin{table}[H]
\centering\small
\caption{Derived constants in \texttt{core/constants.py}.
Every entry traces to Axioms~1--4 with zero free parameters.}
\label{tab:engine_constants}
\begin{tabular}{lll}
\toprule
\textbf{Symbol} & \textbf{Expression} & \textbf{Axiom} \\
\midrule
$Z_0$        & $\sqrt{\mu_0/\varepsilon_0} \approx 376.73\;\Omega$ & 1 \\
$\ell_{node}$ & $\hbar/(m_e c) \approx 3.86 \times 10^{-13}$ m     & 1 \\
$\alpha$      & $e^2/(4\pi\varepsilon_0\hbar c)$                    & 2 \\
$V_{snap}$    & $m_e c^2 \sqrt{\alpha}/e \approx 43.65$ kV          & 4 \\
$B_{snap}$    & $V_{snap}/(c \cdot \ell_{node})$                    & 4 \\
$G$           & $\hbar c / (7\xi \cdot m_e^2)$                      & 3 \\
\bottomrule
\end{tabular}
\end{table}


\subsection{\texttt{axioms/scale\_invariant.py} --- Universal Operators}

This module is the single source of truth for all impedance physics.
Table~\ref{tab:scale_invariant_api} lists every exported function.

\begin{table}[H]
\centering\small
\caption{Complete API of \texttt{scale\_invariant.py}.
Every domain module delegates to these functions.}
\label{tab:scale_invariant_api}
\begin{tabular}{lll}
\toprule
\textbf{Function} & \textbf{Formula} & \textbf{Domain invariance} \\
\midrule
\texttt{impedance($\mu$, $\varepsilon$)}
  & $Z = \sqrt{\mu/\varepsilon}$
  & Vacuum, plasma, seismic, protein \\
\texttt{saturation\_factor($A$, $A_c$)}
  & $\sigma = \sqrt{1-(A/A_c)^2}$
  & Dielectric, BCS, galactic, relativistic \\
\texttt{epsilon\_eff($A$, $A_c$)}
  & $\varepsilon_0 \cdot \sigma$
  & Plasma onset, FDTD \\
\texttt{mu\_eff($B$, $B_c$)}
  & $\mu_0 \cdot \sigma$
  & Meissner, particle confinement \\
\texttt{reflection\_coeff($Z_1$, $Z_2$)}
  & $\Gamma = (Z_2-Z_1)/(Z_2+Z_1)$
  & Pauli, Moho, S$_{11}$, MSW \\
\texttt{transmission\_coeff($Z_1$, $Z_2$)}
  & $T = 1 + \Gamma$
  & All boundaries \\
\texttt{local\_wave\_speed($A$, $A_c$)}
  & $c_{eff} = c_0 (1-r^2)^{1/4}$
  & Phase velocity under saturation \\
\texttt{impedance\_at\_strain($A$, $A_c$)}
  & $Z_{eff} = Z_0 / (1-r^2)^{1/4}$
  & Local impedance under saturation \\
\bottomrule
\end{tabular}
\end{table}


\section{Tier 2: Domain Adapters}
\label{sec:tier2_adapters}

Each domain module provides \emph{only} the constitutive mapping
($\varepsilon$-analog, $\mu$-analog) specific to its physical
domain.  All impedance, saturation, and reflection calculations
delegate to Tier~1.

\subsection{\texttt{gravity/} --- Gravitational Impedance}

\begin{itemize}
    \item \texttt{refractive\_index($M$, $r$)}: $n(r) = 1 + 2GM/(rc^2)$
    \item \texttt{local\_mu($M$, $r$)}: $\mu_{eff} = \mu_0 \cdot n(r)$
    \item \texttt{local\_epsilon($M$, $r$)}: $\varepsilon_{eff} = \varepsilon_0 \cdot n(r)$
    \item \textbf{Key result:} $Z = \sqrt{\mu_{eff}/\varepsilon_{eff}} = Z_0$ (invariant)
    \item Sub-modules: \texttt{solar\_impedance}, \texttt{galactic\_rotation},
          \texttt{gw\_propagation}, \texttt{stellar\_interior},
          \texttt{neutrino\_msw}, \texttt{planetary\_magnetosphere}
\end{itemize}

\subsection{\texttt{plasma/} --- Electromagnetic Saturation}

\begin{itemize}
    \item \texttt{cutoff.py}: Plasma frequency, Drude dielectric function,
          skin depth. Delegates saturation to \texttt{epsilon\_eff}.
    \item \texttt{superconductor.py}: Critical field via
          \texttt{saturation\_factor(T, T\_c)}. Meissner $\mu_{eff}$
          delegates to \texttt{mu\_eff}. London depth, coherence length.
    \item \textbf{Duality:}
          Plasma~=~$\varepsilon\to 0$ (E-field expelled),
          Superconductor~=~$\mu\to 0$ (B-field expelled).
\end{itemize}

\subsection{\texttt{geophysics/} --- Acoustic Impedance}

\begin{itemize}
    \item $\varepsilon$-analog: compressibility $1/K$
    \item $\mu$-analog: shear compliance $1/G$
    \item $Z = \rho V$ (acoustic impedance in Rayl)
    \item Reflection at Moho: $\Gamma \approx 0.17$ via
          \texttt{reflection\_coefficient}
\end{itemize}

\subsection{\texttt{topological/} --- Knot Invariants}

\begin{itemize}
    \item \texttt{borromean.py}: Borromean ring geometry, linking numbers
    \item \texttt{faddeev\_skyrme.py}: Soliton energy functionals
    \item \texttt{cosserat.py}: Micropolar continuum tensors
    \item \texttt{soliton\_bond\_solver.py}: Nuclear bond energy from
          topological winding
\end{itemize}


\section{Tier 3: Solvers}
\label{sec:tier3_solvers}

\subsection{\texttt{core/fdtd\_3d.py} --- 3D Nonlinear FDTD}

The primary FDTD engine.  At each time step, $\varepsilon_{eff}$
and $\mu_{eff}$ are recomputed from the local field amplitudes via
\texttt{saturation\_factor}, implementing Axiom~4 dynamically.

\subsection{\texttt{solvers/bond\_energy\_solver.py} --- Nuclear Bond Curves}

1D FDTD for computing $E(d)$ curves between nuclear defects.
Places mass-modified $\mu$ profiles on the lattice and measures
total electromagnetic energy vs.\ separation.  Extracts equilibrium
distance and force constant $k = d^2E/dd^2$.

\subsection{\texttt{solvers/fdtd\_lc\_network.py} --- Macroscopic Gravity FDTD}

1D transmission-line solver with spatially varying $\varepsilon(r)$
and $\mu(r)$ set by the gravitational refractive index.  Used for
gravitational lensing and wave propagation through curved spacetime.


\section{Delegation Flow}

The following diagram traces a representative computation---the
Meissner reflection coefficient---through all three tiers:

\begin{verbatim}
superconductor.meissner_reflection(B, B_c)
  |-> scale_invariant.mu_eff(B, B_c, mu_base=MU_0)
  |     |-> scale_invariant.saturation_factor(B, B_c)  [Axiom 4]
  |     |-> return MU_0 * S
  |-> scale_invariant.impedance(mu_eff, EPSILON_0)     [Axiom 1]
  |     |-> return sqrt(mu_eff / EPSILON_0)
  |-> scale_invariant.reflection_coefficient(Z_0, Z_sc)
        |-> return (Z_sc - Z_0) / (Z_sc + Z_0)
\end{verbatim}

Every domain computation follows this pattern: domain-specific
inputs $\to$ constitutive mapping $\to$ universal operators.
No scale-specific physics is hard-coded at any level.
