\chapter{The Rosetta Stone of VSI}
\label{app:rosetta_stone}

\section{D.1 The Mapping Table}
The following table provides the definitive translation between classical electrical engineering hardware terms and emergent physical phenomena within the \textit{Discrete Amorphous Manifold} ($M_A$).

\begin{tabularx}{\textwidth}{|l|l|X|}
\hline
\textbf{Hardware Term} & \textbf{Physical Equivalent} & \textbf{VSI Mechanical Role} \\ \hline
Inductance ($L_{node}$) & Inertia ($\mu_{0}$) & Resistance to flux acceleration (Back-EMF). \\ \hline
Capacitance ($C_{node}$) & Elasticity ($\epsilon_{0}$) & Energy storage capacity of the node. \\ \hline
Impedance ($Z_{0}$) & Spacetime Stiffness & $\sqrt{L/C} \approx 377\Omega$. The baseline load. \\ \hline
Impedance Clamping & Weak Force & Rejection of chiral signals by the lattice grain. \\ \hline
Saturation ($\omega_{sat}$) & Rest Mass & Energy trapped in a non-linear node state. \\ \hline
Lattice Pitch ($l_P$) & Planck Length & The fundamental pixel size of the universe. \\ \hline
Lattice Genesis & Dark Energy & The continuous crystallization of new nodes. \\ \hline
Borromean Ring & Proton & A composite knot of 3 flux loops (Quarks). \\ \hline
\end{tabularx}

\section{D.2 Key Descriptive Definitions}
\begin{itemize}
    \item \textbf{Lattice Genesis:} The hypothesis that the vacuum is not expanding geometrically, but actively multiplying (crystallizing) new nodes from the substrate, driven by tension ($P_{vac}$).
    \item \textbf{Pilot Wave:} The localized impedance wake generated by a moving topological defect, guiding its path through deterministic interference.
    \item \textbf{Topological Helicity ($h$):} The quantized, self-reinforcing phase twist of a defect. Replaces the geometric "Winding Number" and identifies Electric Charge.
    \item \textbf{Metric Refraction:} The bending of light paths caused by a variable impedance gradient rather than abstract geometric curvature.
\end{itemize}