\section{Application III: Particles as Resonant LC Tanks}

If empty, undisturbed spacetime is modeled as a passive, linear cascaded transmission line, how do we model the existence of physical matter (Fermions) within the SCA framework? 

As defined in Chapters 3 and 4, a particle is a stable topological defect—a localized, highly tensioned phase vortex permanently locked into the discrete graph structure. In classical electrical engineering, a localized, trapped electromagnetic standing wave that permanently cycles energy is identically defined as a \textbf{Resonant LC Tank Circuit}.

We can computationally verify this by defining a single, localized SPICE tank circuit using the exact translated properties of an electron. 
By applying the Topo-Kinematic mapping to the electron's rest mass, its equivalent localized Inductance is exactly $L_e \equiv \xi_{topo}^{-2} m_e$. The local lattice compliance acts as the restoring capacitor ($C_e \equiv \xi_{topo}^2 k^{-1}$).

When we evaluate this closed-loop tank circuit in the AVE-SPICE ODE solver and apply a transient "pluck," the circuit naturally and organically rings at its fundamental resonant frequency ($\omega_0 = 1/\sqrt{L_e C_e}$). Evaluating this numerically yields a spontaneous harmonic ring frequency of exactly $\mathbf{1.23 \times 10^{20} \text{ Hz}}$. 

This is not a coincidence; it mathematically perfectly recovers the \textbf{Compton Frequency} ($\omega_c = m_e c^2 / \hbar$) of the electron. In the AVE framework, the quantum wave-function of a particle is analytically equivalent to the AC harmonic oscillation of a discrete, localized LC tank ringing in the spacetime substrate.

\subsection{Recovering the Virial Theorem and $E=mc^2$}
We must rigorously evaluate the stored energy of this resonant soliton. The peak internal dynamic (inductive) energy of an LC tank is $E_{mag} = \frac{1}{2} L_e I_{max}^2$. Substituting $I_{max} = \xi_{topo} c$, this evaluates to:
\begin{equation}
    E_{mag} = \frac{1}{2} (\xi_{topo}^{-2} m_e) (\xi_{topo} c)^2 = \mathbf{\frac{1}{2} m_e c^2}
\end{equation}
Notice this yields exactly half the rest mass. This flawlessly resolves the historical "4/3 Electromagnetic Mass Paradox" regarding Poincaré Stresses. In a stable LC resonant soliton, the classical \textbf{Virial Theorem} rigidly dictates that the Capacitive (electric/strain) energy stored in the static topological twist of the core must exactly equal the inductive kinetic energy ($E_{elec} = E_{mag} = \frac{1}{2}m_e c^2$). 

Summing the two energy ledgers yields exactly $E_{total} = m_e c^2$. Einstein's mass-energy equivalence principle is mechanically, rigorously, and mathematically identical to the \textbf{Total Stored Electrical Energy of a Resonant LC Tank Circuit} ringing natively inside the discrete $\mathcal{M}_A$ hardware.