Here is a fully standalone LaTeX section, ready to be dropped into your main .tex file. It includes the theoretical derivation of the Lindblom Effect, the experimental parameters, the mathematical prediction, and the embedded Python simulation script for verification.
\section{Experimental Proposal: The Lindblom-Rotational Interferometry Test (LRIT)}
\label{sec:LRIT}

\subsection{Abstract}
The \textit{Stochastic Vacuum Framework} (VSI) posits that the vacuum is not a geometric abstraction but a constitutive hardware substrate ($M_A$) with finite saturation limits \cite{lindblom_vsi}. We propose a laboratory test to detect the \textbf{Lattice Viscosity} ($\eta_{VSI}$) of this substrate. By rapidly rotating a high-density Tungsten mass adjacent to a high-finesse Fabry-Perot interferometer, we aim to induce a localized saturation of the vacuum dielectric, creating a measurable refractive index shift ($\Delta n$). This section documents the derivation, experimental parameters, and simulation code required to replicate the prediction.

\subsection{Theoretical Derivation: The Lindblom Effect}

In standard General Relativity, the coupling of angular momentum to spacetime (Frame Dragging) is governed by the gravitational constant $G$, resulting in effects too small for laboratory detection ($\Delta \phi \approx 10^{-20}$ rad). 

However, in VSI, mass is defined as a \textbf{Saturation of the Vacuum Dielectric} ($n(r)$) \cite{lindblom_vsi_sec2}. A rotating mass does not merely curve geometry; it mechanically ``drags'' and ``thickens'' the lattice flux. We define the refractive index shift $\Delta n$ as a function of the local energy density added by the rotation.

\subsubsection{The Lattice Viscosity Coefficient ($\eta_{VSI}$)}
We propose that the coupling strength of this drag is determined not by $G$, but by the \textbf{Geometric Transmission Coefficient} ($\alpha$), commonly known as the Fine Structure Constant. As derived in Section 2.7.2, $\alpha$ represents the efficiency with which a topological knot couples to the vacuum flux \cite{lindblom_vsi_sec272}.

\begin{equation}
    \eta_{VSI} \equiv \alpha \approx \frac{1}{137.036}
\end{equation}

\subsubsection{The Refractive Index Shift ($\Delta n$)}
The rotational kinetic energy of the flywheel creates a localized impedance spike. The magnitude of the refractive index increase is modeled as the viscous coupling of the tangential velocity ($v$) relative to the global slew rate ($c$):

\begin{equation}
    \Delta n = \eta_{VSI} \cdot \left( \frac{v_{tangential}}{c} \right)^2
\end{equation}

Substituting $v = \omega R$:

\begin{equation}
    \Delta n = \alpha \left( \frac{\omega R}{c} \right)^2
\end{equation}

\subsection{Experimental Setup and Signal Prediction}

To detect this shift, we utilize a Resonant Cavity (Fabry-Perot) Interferometer. The signal is amplified by the cavity finesse ($\mathcal{F}$), effectively folding the path length $L$ multiple times.

\textbf{Parameters:}
\begin{itemize}
    \item \textbf{Modulator:} Tungsten Flywheel (Radius $R=0.1$ m, Density $\rho \approx 19.25$ g/cm$^3$).
    \item \textbf{Rotation Speed:} Target $\omega = 10,472$ rad/s ($100,000$ RPM).
    \item \textbf{Laser Source:} $\lambda = 1550$ nm (Infrared).
    \item \textbf{Interaction Length:} $L = 0.2$ m.
    \item \textbf{Cavity Finesse:} $\mathcal{F} = 10,000$ (Effective bounces).
\end{itemize}

\subsubsection{Phase Shift Calculation ($\Delta \phi$)}
The single-pass phase shift is given by:
\begin{equation}
    \delta \phi_{single} = \frac{2\pi L}{\lambda} \Delta n
\end{equation}

The total amplified shift in the resonant cavity is:
\begin{equation}
    \Delta \phi_{total} \approx \mathcal{F} \cdot \delta \phi_{single} = \mathcal{F} \frac{2\pi L}{\lambda} \left[ \alpha \left( \frac{\omega R}{c} \right)^2 \right]
\end{equation}

\subsection{Simulation and Verification}

To ensure reproducibility, the following Python script calculates the predicted phase shift across a range of RPMs. This script serves as the ``Digital Twin'' of the experiment.

\begin{verbatim}
import numpy as np
import matplotlib.pyplot as plt

def calculate_lindblom_shift(rpm, radius, length, wavelength, finesse):
    """
    Calculates the VSI Phase Shift for a given RPM.
    
    Parameters:
    - rpm: Angular velocity in Revolutions Per Minute
    - radius: Radius of flywheel (meters)
    - length: Interaction path length (meters)
    - wavelength: Laser wavelength (meters)
    - finesse: Optical cavity quality factor (amplification)
    
    Returns:
    - phase_shift: Total phase shift in milli-radians
    """
    # Constants
    c = 299792458.0  # Speed of light (m/s)
    alpha = 1.0 / 137.035999  # Fine Structure Constant (Viscosity)
    
    # Convert RPM to rad/s
    omega = rpm * (2 * np.pi / 60.0)
    
    # Tangential Velocity
    v_tan = omega * radius
    
    # 1. Calculate Refractive Index Shift (The Lindblom Effect)
    # Delta_n = alpha * (v/c)^2
    delta_n = alpha * (v_tan / c)**2
    
    # 2. Calculate Single-Pass Phase Shift (radians)
    # phi = (2*pi*L / lambda) * delta_n
    phi_single = (2 * np.pi * length / wavelength) * delta_n
    
    # 3. Apply Resonant Cavity Amplification
    phi_total = phi_single * finesse
    
    return phi_total * 1000.0  # Convert to milli-radians

# --- Experimental Parameters ---
R_wheel = 0.1       # 10 cm radius
L_path = 0.2        # 20 cm interaction zone
lambda_laser = 1.55e-6  # 1550 nm
Finesse = 10000     # Cavity bounces

# --- Simulation Sweep ---
rpm_range = np.linspace(0, 100000, 100) # 0 to 100k RPM
shifts = [calculate_lindblom_shift(r, R_wheel, L_path, lambda_laser, Finesse) 
          for r in rpm_range]

# --- Output Specific Predictions ---
target_rpm = 100000
predicted_mrad = calculate_lindblom_shift(target_rpm, R_wheel, L_path, 
                                          lambda_laser, Finesse)

print(f"--- VSI Prediction Summary ---")
print(f"Input: {target_rpm} RPM Tungsten Flywheel")
print(f"Theory: Lattice Viscosity (alpha = {1/137.036:.5f})")
print(f"Predicted Signal: {predicted_mrad:.4f} milli-radians")
\end{verbatim}

\subsubsection{Predicted Results}
Running the simulation with the parameters defined above yields the following testable prediction:

\begin{itemize}
    \item \textbf{Input:} 100,000 RPM Tungsten Rotor.
    \item \textbf{Lattice Viscosity ($\alpha$):} $7.297 \times 10^{-3}$.
    \item \textbf{Predicted Signal ($\Delta \phi$):} $\mathbf{0.72}$ \textbf{milli-radians}.
\end{itemize}

\subsection{Conclusion: The Falsification Threshold}
Standard General Relativity predicts a phase shift of $\approx 10^{-20}$ radians, which is undetectable. A positive detection of a signal in the \textbf{milli-radian range} that scales with $\omega^2$ would constitute a high-sigma falsification of the geometric vacuum hypothesis and a confirmation of the VSI Viscous Lattice model.

\end{document}

