\section{Constitutive Circuit Models for Vacuum Non-Linearities}
\label{sec:vca_nonlinear}

Standard circuit simulators rely on ideal, linear RLC components. However, the physical $\mathcal{M}_A$ condensate exhibits precise non-linear behaviors under extreme mechanical stress, each governed by the Axiom~4 saturation kernel $S(V) = \sqrt{1-(V/V_{yield})^2}$. This section derives the exact non-linear equivalent circuit component for each physical regime.

\subsection{The Metric Varactor (Dielectric Yield)}

As defined by Axiom~4, the effective compliance (capacitance) of the spatial substrate is bounded by the dielectric saturation limit at $V_{yield} = \sqrt{\alpha}\, V_{snap} \approx 43.65$ kV. The constitutive equation follows directly from the saturation kernel applied to the electric sector:
\begin{resultbox}{Vacuum Varactor Constitutive Equation}
\begin{equation}
    C_{eff}(V) = \frac{C_0}{\sqrt{1 - \left(\dfrac{V}{V_{yield}}\right)^{\!2}}} = \frac{C_0}{S(V)}
    \label{eq:varactor}
\end{equation}
\end{resultbox}

To verify consistency with the weak-field limit, the Taylor expansion about $V = 0$ yields:
\begin{equation}
    C_{eff}(V) = C_0 \left[1 + \frac{1}{2}\left(\frac{V}{V_{yield}}\right)^{\!2} + \frac{3}{8}\left(\frac{V}{V_{yield}}\right)^{\!4} + \cdots\right]
    \label{eq:varactor_taylor}
\end{equation}
At low voltages ($V \ll V_{yield}$), the leading correction is quadratic---identical to the Euler-Heisenberg effective Lagrangian of QED. The classical linear vacuum ($C_{eff} = C_0$) is recovered to arbitrary precision. Table~\ref{tab:varactor_values} evaluates the capacitance divergence at representative drive levels.

\begin{table}[H]
\centering
\caption{Effective vacuum capacitance vs.\ drive level. The divergence accelerates sharply above 90\% of $V_{yield}$.}
\label{tab:varactor_values}
\small
\begin{tabular}{@{}r r r r@{}}
\toprule
$V/V_{yield}$ & $V$ (kV) & $C_{eff}/C_0$ & $S(V)$ \\
\midrule
0.10  &  4.37  & 1.005 & 0.995 \\
0.50  & 21.83  & 1.155 & 0.866 \\
0.90  & 39.29  & 2.294 & 0.436 \\
0.99  & 43.21  & 7.089 & 0.141 \\
0.999 & 43.61  & 22.37 & 0.045 \\
1.000 & 43.65  & $\infty$ & 0  \\
\bottomrule
\end{tabular}
\end{table}

\subsection{The Relativistic Inductor (Lorentz Saturation)}

Under the Topo-Kinematic identity, mass maps to inductance ($L = \xi_{topo}^{-2}\, m$) and velocity maps to current ($I = \xi_{topo}\, v$). The relativistic mass increase $m_{eff} = \gamma\, m_0$ therefore maps directly to a current-dependent inductance:
\begin{resultbox}{Relativistic Inductor}
\begin{equation}
    L_{eff}(I) = \frac{L_0}{\sqrt{1 - \left(\dfrac{I}{I_{max}}\right)^{\!2}}}, \qquad I_{max} = \xi_{topo}\, c \approx 124.4 \text{ A}
    \label{eq:relativistic_inductor}
\end{equation}
\end{resultbox}

This is structurally identical to the varactor equation (Eq.~\ref{eq:varactor}), with the substitution $V \to I$ and $V_{yield} \to I_{max}$. The symmetry is not coincidental: both are projections of the single Axiom~4 kernel onto the electric and magnetic sectors, respectively.

\paragraph{Derivation of $E = mc^2$.}
The energy stored in a current-carrying inductor is $E = \tfrac{1}{2} L_{eff}\, I^2$. Expanding at low velocity ($v \ll c$):
\begin{equation}
    E = \frac{1}{2} \frac{L_0}{\sqrt{1-(v/c)^2}}\, (\xi_{topo}\, v)^2 = \frac{1}{2} \gamma\, \xi_{topo}^{-2}\, m_0\, \xi_{topo}^2\, v^2 = \frac{1}{2} \gamma\, m_0\, v^2
\end{equation}
At $v = 0$, the rest energy stored in the inductor's self-field is $E_0 = \tfrac{1}{2} L_0 I_{max}^2 = \tfrac{1}{2} (\xi_{topo}^{-2} m_0)(\xi_{topo} c)^2 = \tfrac{1}{2} m_0 c^2$. Summing with the capacitive (potential) energy via the Virial Theorem recovers $E_{total} = m_0 c^2$.

\paragraph{Why SPICE Cannot Exceed $c$.}
In a standard SPICE transient simulation, the inductor $L_0$ limits the current slew rate to $dI/dt = V/L$. As $I \to I_{max}$, $L_{eff} \to \infty$, and the slew rate collapses to zero. The circuit physically cannot push current (matter) past the hardware limit. SPICE engines natively enforce Special Relativity without any code modification.

\subsection{The Viscoelastic TVS Zener Diode (Phase Transition)}

Mutual inductance yields when the applied shear stress exceeds the structural threshold ($\tau > \tau_{yield}$). This voltage-driven breakdown maps exactly to a \textbf{Transient Voltage Suppression (TVS) Zener Diode}:

\begin{resultbox}{TVS Breakdown: Solid $\to$ Slipstream Transition}
\begin{equation}
    \eta_{eff}(V) = \begin{cases}
        \eta_0 & V < V_{yield} \quad \text{(solid: high drag)} \\[4pt]
        0      & V \geq V_{yield} \quad \text{(slipstream: zero drag)}
    \end{cases}
    \label{eq:tvs_transition}
\end{equation}
\end{resultbox}

Below the yield voltage, the vacuum acts as a highly resistive solid---kinematically gripping embedded matter via inductive drag ($\eta_0 > 0$). Above $V_{yield}$, an avalanche dielectric transition annihilates the mutual inductance. The vacuum enters ideal frictionless flow ($\eta = 0$): the \textbf{Zero-Impedance Slipstream}. The yield stress evaluates from the bulk energy density and packing geometry:
\begin{equation}
    \tau_{yield} = \rho_{bulk}\, c^2 \times (6 \times \mathcal{V}_{crossing}) \times \frac{p_c}{8\pi} \approx 7.91 \times 10^{6} \times (3 \times 10^8)^2 \times 1.326 \times 0.00730
\end{equation}
where $\mathcal{V}_{crossing} = V_{toroidal}/6 = 2.0/6$ is the per-crossing halo volume and $p_c/(8\pi) = \alpha \approx 1/137$ is the lattice porosity.

\subsection{The Vacuum Memristor (Thixotropic Hysteresis)}

The dielectric saturation--plastic transition requires a finite geometric relaxation time to physically liquefy the lattice:
\begin{resultbox}{Thixotropic Relaxation Time}
\begin{equation}
    \tau_{relax} = \frac{\ell_{node}}{c} = \frac{3.862 \times 10^{-13}}{2.998 \times 10^{8}} \approx 1.288 \times 10^{-21} \text{ s}
    \label{eq:relaxation_time}
\end{equation}
\end{resultbox}

Because the vacuum cannot alter its inductive resistance instantaneously, its present-state impedance depends on the historical integral of applied stress. This is the defining characteristic of a \textbf{Memristor}: a circuit element whose resistance is a function of the cumulative charge that has passed through it.

The constitutive relation is:
\begin{equation}
    M(q) = \frac{d\Phi}{dq}, \qquad \Phi(t) = \int_{-\infty}^{t} V(\tau)\, d\tau
    \label{eq:memristor_constitutive}
\end{equation}
where $M$ is the memristance (units: $\Omega$) and $\Phi$ is the magnetic flux linkage. Under high-frequency AC topological stress, the memristive vacuum produces a classic \textbf{Pinched Hysteresis Loop}: the $V$--$I$ Lissajous figure passes through the origin but encloses a finite area proportional to the energy dissipated during each thixotropic yield--heal cycle.

At drive frequencies $f \gg 1/\tau_{relax} \approx 7.8 \times 10^{20}$ Hz, the vacuum responds too slowly to yield and behaves as a purely elastic (linear) medium. At $f \ll 1/\tau_{relax}$, complete yield and recovery occur within each cycle, producing maximum hysteresis loss. The crossover frequency is set entirely by the lattice pitch and $c$.

\subsection{The Zero-Impedance Skin Effect (Metric Faraday Cages)}

In standard electrical engineering, the AC skin depth $\delta$ governs how deeply alternating current penetrates into a conductor:
\begin{resultbox}{Classical Skin Depth}
\begin{equation}
    \delta = \sqrt{\frac{2\rho}{\omega\mu}} = \sqrt{\frac{2 R_{vac}}{\omega\mu_0}}
    \label{eq:skin_depth}
\end{equation}
\end{resultbox}

Under the Topo-Kinematic identity, $R_{vac} \equiv \xi_{topo}^{-2}\, \eta_{vac}$: the vacuum's electrical resistance maps to its mutual inductance (drag coefficient). Evaluating the skin depth in the two vacuum phases:

\begin{enumerate}
    \item \textbf{Unsaturated Vacuum ($V < V_{yield}$):} $R_{vac} = \xi_{topo}^{-2}\, \eta_0 > 0$. The skin depth is finite; shear waves penetrate to a depth proportional to $\sqrt{\eta_0}$. At 1~GHz:
    \begin{equation}
        \delta_{solid} = \sqrt{\frac{2\, \xi_{topo}^{-2}\, \eta_0}{2\pi \times 10^9 \times \mu_0}} \sim \text{finite (deep-space penetration)}
    \end{equation}

    \item \textbf{Saturated Slipstream ($V \geq V_{yield}$):} $\eta_{eff} \to 0$, therefore $R_{vac} \to 0$:
    \begin{equation}
        \delta_{slipstream} = \sqrt{\frac{2 \times 0}{\omega\mu_0}} \equiv 0
    \end{equation}
\end{enumerate}

When the metric exceeds the yield threshold, the skin depth collapses to zero. The destructive, high-shear slipstream is confined \textit{entirely} to the exterior surface of the macroscopic body. The interior metric acts as a \textbf{Topological Faraday Cage}: perfectly shielded from external structural shear, even at extreme gravitational gradients. This provides the mechanical basis for why planetary interiors remain structurally intact inside deep gravity wells.
