\section{The Weak Interaction: Micropolar Cutoff Dynamics}
\label{sec:weak_interaction}

The Weak Force is unique because it is extraordinarily short-range ($\approx 10^{-18}$ m) and mediated by massive gauge bosons ($W \approx 80.4$ GeV, $Z \approx 91.2$ GeV). The Standard Model explains this via the Higgs Mechanism. DCVE derives this natively from the \textbf{Characteristic Cutoff Scale} of the Cosserat vacuum continuum.

\subsection{The Flaw of Harmonic Numerology}
Previous versions of this text attempted to derive the W and Z boson masses by multiplying the proton mass by arbitrary geometric fractions (e.g., $5/8$ and $3/\sqrt{7}$). This phenomenological numerology is mathematically devoid of dynamical justification and must be completely abandoned.

\subsection{Rigorous Derivation: The Cosserat Cutoff Length}
In Chapter 7, we established that the vacuum substrate is a Cosserat (Micropolar) Continuum. Such a medium possesses not only a shear modulus ($\mu$) but also a microrotational stiffness ($\gamma_c$). 

In any Cosserat solid, the ratio of the bending/rotational stiffness to the shear modulus defines a fundamental \textbf{Characteristic Length Scale} ($l_c$), which dictates the spatial extent to which localized couple-stresses (twists) can propagate before exponentially decaying:
\begin{equation}
    l_c = \sqrt{\frac{\gamma_c}{\mu}}
\end{equation}
We formally identify this mechanical decay length $l_c$ as the physical range of the Weak Force ($r_W \approx 10^{-18}$ m). 

\subsection{Deriving the W and Z Boson Masses}
The gauge bosons of the Weak interaction are not point particles flying through an empty void; they are the fundamental energetic excitations required to induce a localized phase twist at this absolute cutoff scale. The mass of the $W$ boson is strictly defined by the acoustic energy required to excite a rotational mode of wavelength $\lambda = l_c$ in the lattice:
\begin{equation}
    m_W = \frac{\hbar}{l_c c}
\end{equation}

The difference between the $W$ and $Z$ boson masses is governed by the \textbf{Weak Mixing Angle} ($\theta_W$). In the Cosserat vacuum, this angle is not a free parameter of a unified gauge group; it is the exact physical ratio between the longitudinal torsional stiffness and the transverse rotational stiffness of the discrete lattice links.
\begin{equation}
    \cos \theta_W = \frac{m_W}{m_Z} = \sqrt{\frac{\text{Torsional Stiffness}}{\text{Bending Stiffness}}}
\end{equation}

\textbf{Conclusion:} The Weak Force does not require an abstract Higgs field to attain mass. The massive $W$ and $Z$ bosons are the direct mechanical consequence of the intrinsic structural rigidity of the micropolar vacuum. They are heavy because twisting a physical lattice at the scale of $10^{-18}$ meters requires immense acoustic energy.