\section{The Nyquist Limit: Recovering Lorentz Invariance}

A central critique of discrete spacetime models is the potential violation of Lorentz Invariance. If the vacuum is a discrete grid, why do we observe continuous isotropic laws of physics? We explicitly derive the Effective Field Theory (EFT) limit of the AVE substrate to mathematically prove that Special Relativity emerges perfectly as the Infrared (IR) fixed point of the lattice.

For a plane wave solution traversing a discrete lattice with mean pitch $l_{node}$, the discrete Laplacian operator natively induces a frequency-dependent dispersion relation:
\begin{equation}
    \omega(k) = \frac{2c}{l_{node}} \sin\left(\frac{k l_{node}}{2}\right)
\end{equation}

The speed at which physical information travels is the Group Velocity $v_g = \frac{\partial \omega}{\partial k}$. Differentiating the hardware dispersion relation yields:
\begin{equation}
    v_g(k) = c \cos\left(\frac{k l_{node}}{2}\right) \approx c \left[ 1 - \frac{1}{8}(k l_{node})^2 + \mathcal{O}(k^4) \right]
\end{equation}

Because the physical lattice pitch is anchored rigidly at $l_{node} \approx 3.74 \times 10^{-19}$ m, for all standard low-energy physics, the term $(k l_{node})^2$ mathematically vanishes. 
\begin{equation}
    \lim_{k \to 0} v_g(k) = c
\end{equation}

Lorentz Invariance is not an axiomatic fundamental symmetry of the substrate; it is the rigorous \textbf{Low-Energy Equilibrium (IR Fixed Point)} of the lattice dynamics. The vacuum appears continuous simply because our experimental wavelengths are too large to mechanically resolve the discrete grain. 

\textbf{Falsification Condition:} The un-truncated dispersion relation predicts that ultra-high-energy Trans-Planckian signals (e.g., extreme Gamma Ray Bursts) must arrive slightly later than their low-energy counterparts emitted simultaneously. If future observatories confirm strictly energy-independent arrival times across the absolute spectrum, the discrete graph is falsified.