\section{The Nyquist Limit: Recovering Lorentz Invariance}
\label{sec:nyquist_limit}

A central critique of discrete spacetime models is the potential violation of Lorentz Invariance. If the vacuum is a grid, why do we observe isotropic laws of physics? We explicitly derive the \textit{Effective Field Theory (EFT)} limit of the AVE substrate to show that Special Relativity emerges as the Infrared (IR) fixed point of the lattice dynamics.

\subsection{The Discrete Dispersion Relation}
Consider the propagation of a scalar signal $\phi$ across the discrete graph $\mathcal{G}$. From Axiom III (The Discrete Action Principle), the equation of motion for a node $n$ connected to neighbors $j$ via edge lengths $l_{nj}$ is:
\begin{equation}
\partial_t^2 \phi_n = \frac{c^2}{l_{node}^2} \sum_{j} (\phi_j - \phi_n)
\end{equation}
For a plane wave solution $\phi(x,t) = A e^{i(kx - \omega t)}$ traversing a lattice with mean pitch $l_{node}$, the discrete Laplacian operator induces a frequency-dependent dispersion relation. In the simplest 1D approximation (Von Neumann Stability Analysis):
\begin{equation}
\omega(k) = \frac{2c}{l_{node}} \sin\left(\frac{k l_{node}}{2}\right)
\end{equation}
This is the fundamental \textit{Hardware Dispersion Relation} of the vacuum.

\subsection{Group Velocity and the Speed of Light}
The speed at which information travels is the Group Velocity $v_g = \frac{\partial \omega}{\partial k}$. Differentiating the dispersion relation:
\begin{equation}
v_g(k) = c \cos\left(\frac{k l_{node}}{2}\right)
\end{equation}
We now apply the \textit{Continuum Limit} where the wavelength $\lambda$ is macroscopic compared to the lattice pitch ($\lambda \gg l_{node}$, or $k l_{node} \ll 1$). Expanding the cosine term:
\begin{equation}
v_g(k) \approx c \left[ 1 - \frac{1}{8}(k l_{node})^2 + \mathcal{O}(k^4) \right]
\end{equation}

\subsubsection{Recovering the Continuum (IR Fixed Point)}
For all standard physical processes (Standard Model physics), the energy scale $E$ is orders of magnitude below the Planck scale breakdown voltage ($l_{node} \approx 10^{-35}$ m).
\begin{equation}
k l_{node} \approx \frac{10^{-18} \text{ m}}{10^{-35} \text{ m}} = 10^{-17} \approx 0
\end{equation}
Consequently, the dispersion term $\frac{1}{8}(k l_{node})^2$ vanishes.
\begin{equation}
\lim_{k \to 0} v_g(k) = c
\end{equation}
\textbf{Conclusion:} Lorentz Invariance is not a fundamental symmetry of the substrate; it is the \textit{Low-Energy Equilibrium} (IR Fixed Point) of the lattice. The vacuum \textit{appears} continuous and isotropic to us simply because our experimental probes are too large to feel the grain.

\subsection{Isotropy via Stochastic Averaging}
A regular cubic lattice breaks rotational symmetry (the "Manhattan Distance" problem). However, Axiom I defines the manifold as an \textit{Amorphous} Delaunay triangulation of a Poisson distribution.
According to the theorem of \textit{Homogenization of Random Media}, the effective wave operator $\mathcal{L}_{eff}$ for a stochastic graph converges to the isotropic Laplacian $\nabla^2$ on scales $L \gg l_{node}$:
\begin{equation}
\langle \mathcal{G}_{random} \rangle \xrightarrow{L \to \infty} \text{Isotropic Continuum}
\end{equation}
The "Jaggedness" of the individual photon paths averages out to a perfect straight line (geodesic) over macroscopic distances, preserving the rotational symmetry observed in nature.

\subsection{The Falsification: Trans-Planckian Dispersion}
While the lattice mimics Special Relativity at low energies, the dispersion relation predicts specific deviations at ultra-high energies ($E \sim E_{Planck}$).
\begin{equation}
\Delta t_{arrival} \approx \frac{L}{c} \cdot \frac{1}{8} (k l_{node})^2
\end{equation}
\textbf{Kill Switch:} If the vacuum is a discrete lattice, high-energy Gamma Ray Bursts (GRBs) should arrive slightly \textit{later} than their low-energy counterparts emitted simultaneously, due to the $\cos(kl_{node})$ slowing factor.
\begin{itemize}
    \item \textbf{AVE Prediction:} Energy-dependent time-of-flight delays for Trans-Planckian signals.
    \item \textbf{Standard Model Prediction:} No dispersion ($v=c$ for all $E$).
\end{itemize}
Current observations (Fermi LAT) constrain $l_{node} < 1.6 \times 10^{-35}$ m. If future detectors measure a strictly energy-independent speed of light even at the Planck scale, the Discrete Manifold hypothesis is falsified.